### 2017-10-29 dl-style-transfer/reports/src/project_report_one.tex
Made project report

\documentclass{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

\usepackage[margin=1in]{geometry}

\usepackage{amsmath}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

\title{Neural Style Transfer on Text\\Project Report One}

\author{Yuji Akamoto, Ryan Butler, Cameron Ibrahim, Luca Leeser}

\begin{document}

\maketitle

\section*{Abstract}

The current state of the project is rather fluid. Having studied current advances
in Style Trasfer and recreated Gatys' original model, we are currently studying
the feasibility of style transfer on text using a similar method. There are a number
of obstacles in this regard, including finding a feasible model for text reconstruction,
studying the properties of style in text, and the possibility of connecting these
two concepts in an extension of existing style transfer work. This group is currently
working on the development of

\section{Introduction}

The current objective of our work has been to research the viability of a variety of text representation models, and the viability of text reconstruction using these methods. Work has been done in using CNNs and autoencoders for text representation. Currently,
the models are still in the process of being implemented, an analysis of their viability for text representation is pending.

\section{Methods and Results}

At this point in the process, the team is still constructing a number of different models
for text representation. Viable candidates include, CNNs, Varaitional Autoencoders, and KATE. Using these, we will study the possiblity of text representation over the next week.

\section{Individual Work}

\begin{description}

	\item [Yuji Akamoto]
		Created a CNN for text representation.

	\item [Ryan Butler]

	\item [Cameron Ibrahim]
		Attempting to implement the KATE autoencoder.
		Generated vector representations of the Yelp review vocabulary.

	\item [Luca Leeser]
		Implemented a variational autoencoder.

\end{description}

\section{Further Studies}

We intend to study the layer by layer representation of text in our models and intend to implement text reconstruction. From there, we will begin to study style representation of text.

\section{References}

\begin{thebibliography}{9}
	\bibitem{Neural Style}
	Leon A. Gatys, Alexander S. Ecker, Matthias Bethge.
	\textit{A Neural Algorithm of Artistic Style}.
	CoRR, 2015.

	\bibitem{Style Transfer Summary}
	Yongcheng Jing, Yezhou Yang, Zunlei Feng, Jingwen Ye, Mingli Song.
	\textit{Neural Style Transfer: A Review}.
	CoRR, 2017.

	\bibitem{Generative models}
	Justin Johnson, Alexandre Alahi, Fei-Fei Li.
	\textit{Perceptual Losses for Real-Time Style Transfer and Super-Resolution}.
	Stanford University.

	\bibitem{Markovian GANs}
	Chuan Li, Michael Wand.
	\textit{Precomputed Real-Time Texture Synthesis with Markovian Generative Adversarial Networks}.
	CoRR, 2016.

	\bibitem{Writing Style Conversion}
	Se Wong Jang, Jesik Min, Mark Kwon.
	\textit{Writing Style Conversion using Neural Machine Translation}.
	Stanford University.

	\bibitem{Text style transfer}
	Tianxiao Shen, Tao Lei, Regina Barzilay, Tommi Jaakkola.
	\textit{Style Transfer from Non-Parallel Text by Cross-Alignment}.
	CoRR, 2017.

	\bibitem{Autoencoder}
	Barak Oshri, Nishith Khandwala.
	\textit{There and Back Again: Autoencoders for Textual Reconstruction}.
	Stanford University.

	\bibitem{KATE}
	Yu Chen, Mohammed J. Zaki.
	\textit{KATE: K-Competitive Autoencoder for Text}. Rensselaer Polytechnic Institute.

\end{thebibliography}

\end{document}

### 2017-10-29 dl-style-transfer/h5vggtopython.py

@@ -1,6 +1,9 @@
 import h5py
 import numpy as np
 
+# A file to convert the cifar10vgg.h5 preset weights
+# to a numpy representation
+
 f = h5py.File("cifar10vgg.h5", "r+")
 
 layer_labels = f.attrs['layer_names']

### 2017-10-29 dl-style-transfer/reports/src/project_report_one.tex
FIxed name
Update project_report_one.tex

@@
 
-\author{Yuji Akamoto, Ryan Butler, Cameron Ibrahim, Luca Leeser}
+\author{Yuji Akimoto, Ryan Butler, Cameron Ibrahim, Luca Leeser}
 
@@
 
-	\item [Yuji Akamoto]
-		Created a CNN for text representation.
+	\item [Yuji Akimoto]
+		Implemented image style transfer with VGG-16 trained on CIFAR-10 data instead of ImageNet data, to see if ``content'' representations of images would still be general enough.
+Also implemented (untrained) ``Shallow-CNN'', a popular convolutional architecture for text classification as described by [Yoon Kim](https://arxiv.org/abs/1408.5882).
 
@@
 
+	\bibitem{Shallow-CNN}
+	Yoon Kim.
+	\textit{Convolutional Neural Networks for Sentence Classification}. CoRR, 2014.
+
 \end{thebibliography}

### 2017-11-10 topic_over_time/workspace/neural_net.py
tensorboard embedding compatible

@@ -18,6 +18,9 @@ def gen_data(ids):
     return np.array(out)
 
 def one_hot(stars):
+    '''
+    build one hot encoding for the star rating
+    '''
     res = []
     for s in stars:
         out = np.array([0.0]*5)
@@ -26,6 +29,12 @@ def one_hot(stars):
     return np.array(res)
 
 def one_hot_three(stars):
+    '''
+    build a 3 class encoding for the easier learning
+    0: 1 star
+    1: 2-4 stars
+    2: 5 stars
+    '''
     res = []
     for s in stars:
         out = np.array([0.0]*3)
@@ -80,9 +89,10 @@ def build_model(x, input_size, hidden, out_size):
         prev = i
 
     # build an output layer
+    embedding_in = activation
     out = output_layer(activation, hidden[-1], out_size, 'output')
 
-    return out
+    return out, embedding_in
 
 
 if __name__ == '__main__':
@@ -91,6 +101,7 @@ if __name__ == '__main__':
 
     lda =  models.LdaModel.load('gensim/lda.model')
     dictionary = corpora.Dictionary.load('gensim/chinsese_dict.dict')
+
     model = Gensimembedder(model = lda, dictionary = dictionary)
 
     case_review = reviews[reviews['business_id'] == 'yfxDa8RFOvJPQh0rNtakHA']
@@ -104,8 +115,13 @@ if __name__ == '__main__':
 
     x = tf.placeholder(tf.float32, shape = [None, 128], name = 'input_topic') # number of topics
     y = tf.placeholder(tf.float32, shape = [None, 3], name = 'softmax') # 5 stars
+
     learning_rate = 0.05
-    out = build_model(x, 128, [100, 100], 3) # shape of (?, 5)
+    hidden_layer = [100, 80, 60]
+
+    embedded_size = hidden_layer[-1]
+
+    out, embedding_in = build_model(x, 128, hidden_layer, 3) # shape of (?, 5)
 
     # loss
     with tf.name_scope("loss"):
@@ -121,14 +137,34 @@ if __name__ == '__main__':
 
 
 
-    training_epoch = 50000
+    training_epoch = 150000
 
 
     with tf.Session() as sess:
         summ = tf.summary.merge_all()
-        writer = tf.summary.FileWriter("tmp/log/1")
+
+        embedding = tf.Variable(tf.zeros([1000, embedded_size]), name = 'embedding')
+        assignment = embedding.assign(embedding_in)
+        saver = tf.train.Saver()
+
[…]

### 2017-11-12 dl-style-transfer/reports/src/project_report_another_one.tex
Wrote project report

--- 2017-10-29 dl-style-transfer/reports/src/project_report_one.tex
@@
 
-The current state of the project is rather fluid. Having studied current advances
-in Style Trasfer and recreated Gatys' original model, we are currently studying
-the feasibility of style transfer on text using a similar method. There are a number
-of obstacles in this regard, including finding a feasible model for text reconstruction,
-studying the properties of style in text, and the possibility of connecting these
-two concepts in an extension of existing style transfer work. This group is currently
-working on the development of
+The exploratory period of this project is quickly coming to a close, and we're ramping up our 
+effort to get definite results. At this time, we are likely going to be using a CNN based
+architecture, in collaboration with competitive layers - either integrated into the layers of the CNN themselves,
+or added to the end of the network, as in the style of the Fully Connected Nets commonly added to the end of CNN
+architectures. Additionally, we are currently putting together a dataset of alternative text sources, to address
+our need for more distinct styles for experiment purposes. We will be training an initial CNN architecture later
+today.
 
@@
 
-The current objective of our work has been to research the viability of a variety of text representation models, and the viability of text reconstruction using these methods.
-Work has been done in using CNNs and autoencoders for text representation.
-Currently,
-the models are still in the process of being implemented, an analysis of their viability for text representation is pending.
+Our current research has moved into a more experimental stage, as we begin to train the inital models we have created. These experiments will be
+use a 10 book dataset of distinct styles. The hope is that this will allow us to more easily determine success and failure. Failure here would 
+render our model unviable for use with Yelp
 
@@
 
-At this point in the process, the team is still constructing a number of different models
-for text representation. Viable candidates include, CNNs, Varaitional Autoencoders, and KATE. Using these, we will study the possiblity of text representation over the next week.
+We are currentlly in the process of training our initial models to begin experiments. Loss function has shown improvement. Created a 10 book dataset of sentences
+for training uses.
 
@@
 
-	\item [Yuji Akamoto]
-		Created a CNN for text representation.
+	\item [Yuji Akimoto]
+		Improved an initial CNN based architecture for text representation. Has yet to be trained.
 
 	\item [Ryan Butler]
+		Further research into KATE, Discrete Autoencoders, and other methods we may be interested in incorporating into our model.
 
 	\item [Cameron Ibrahim]
-		Attempting to implement the KATE autoencoder.
-		Generated vector representations of the Yelp review vocabulary.
+		Assembling the dataset of a number of books pulled from Project Gutenberg. Training Yuji's model. Generated word embeddings for dataset.
 
 	\item [Luca Leeser]
-		Implemented a variational autoencoder.
+		Further refined the facenet L2 based loss function for use with text.
 
@@
 
-We intend to study the layer by layer representation of text in our models and intend to implement text reconstruction. From there, we will begin to study style representation of text.
-
+In the event of total failure of our models, we will pivot to trying to explain exactly \emph{why} our methods have not worked.
+This in itself would make up an interesting research topic, and would easily fill the paper.
 \section{References}

### 2017-11-12 dl-style-transfer/reports/src/project_report_another_one.tex
Updated project report

@@
 	\item [Ryan Butler]
-		Further research into KATE, Discrete Autoencoders, and other methods we may be interested in incorporating into our model.
+		Further research into KATE, Discrete Autoencoders, ResNet, and Inception/Google to search
+		for methods we may be interested in incorporating into our model.
 

### 2017-11-13 topic_over_time/workspace/text_embedder.py
wrapper file for text embedding

@@ -1,0 +1,233 @@
+'''
+Topic-based Text embedding class for Round 10 Yelp Dataset Challenge
+'''
+
+import pandas as pd
+import gensim
+from gensim.utils import simple_preprocess
+from gensim import corpora, models, similarities
+from gensim.parsing.preprocessing import STOPWORDS
+import nltk
+import numpy as np
+
+class TextEmbedder(object):
+    def __init__(self, **kwargs):
+        self.trained = True
+        self.business_idf = False
+        self.user_idf = False
+        if kwargs != None:
+            # load dictionary if exists
+            if 'dictionary' not in kwargs.keys():
+                self.dictionary = None
+                self.trained = False
+            else:
+                self.dictionary = kwargs['dictionary']
+
+            # load topic model if exists
+            if 'model' not in kwargs.keys():
+                self.model = None
+                self.trained = False
+            else:
+                self.model = kwargs['model']
+
+            # load user_idf if exists
+            if 'user_idf' not in kwargs.keys():
+                self.user_idf_dict = None
+            else:
+                self.user_idf_dict = kwargs['user_idf']
+                self.user_idf = True
+
+            # load user_idf if exists
+            if 'business_idf' not in kwargs.keys():
+                self.business_idf_dict = None
+            else:
+                self.business_idf_dict = kwargs['business_idf']
+                self.business_idf = True
+
+
+    def tokenize_(self, text):
+        '''
+        tokenize the text using the utils from Gensim
+
+        Input:
+            text(str) : text that you want to tokenize
+        Output
+            (list): tokenized text
+        '''
+        return [token for token in simple_preprocess(text) if token not in STOPWORDS]
+
+    def embed(self, text, minimum_probability = None):
+        '''
+        embed the raw text into the vector with the length of topic number
+
+        Input:
+            text(str) : text that you want to embed
+        Output:
+            (list): embedded text
+        '''
+        if self.trained:
+            model = self.model
+            dictionary = self.dictionary
+            text = self.tokenize_(text)
+            bow = self.dictionary.doc2bow(text)
+            kindex = self.model.get_document_topics(bow, minimum_probability)
+            out = [0.] * self.model.num_topics
+            for i, p in kindex:
+                out[i] = p
+            return np.array(out)
+        else:
+            print ('Load LDA model and dictionary')
+            return None
+
+
+    def embed_sent(self, text, minimum_probability = None):
+        '''
+        tokenize the text by sentences first, then
[…]

### 2017-11-13 topic_over_time/workspace/text_embedder.py
fixed bug

@@ -9,6 +9,7 @@ from gensim import corpora, models, similarities
 from gensim.parsing.preprocessing import STOPWORDS
 import nltk
 import numpy as np
+import pickle
 
 class TextEmbedder(object):
     def __init__(self, **kwargs):
@@ -151,7 +152,7 @@ class TextEmbedder(object):
             print ('Load LDA model and dictionary')
             return None
 
-     def user_tfidf_embed(self, text, user_id, alpha = 0.5, minimum_probability = 0.0):
+    def user_tfidf_embed(self, text, user_id, alpha = 0.5, minimum_probability = 0.0):
         '''
         embed the text with tf-idf of the topic values for each user
         This will scale the embedding by penalizing frequently mentioned
@@ -159,7 +160,7 @@ class TextEmbedder(object):
         '''
         # for now not allowing this function without loading idf
         if self.trained and self.user_idf:
-            tf = self.augmented_embed_sent(text, alpha, minimum_probability)
+            tf = self.augmented_embed_text(text, alpha, minimum_probability)
             idf = self.user_idf_dict[user_id]
             out = np.multiply(tf, idf)
             if sum(out) == 0.0:
@@ -178,7 +179,7 @@ class TextEmbedder(object):
         '''
         # for now not allowing this function without loading idf
         if self.trained and self.business_idf:
-            tf = augmented_embed_sent(text, alpha, minimum_probability)
+            tf = self.augmented_embed_text(text, alpha, minimum_probability)
             idf = self.business_idf_dict[business_id]
             out = np.multiply(tf, idf)
             if sum(out) == 0.0:
@@ -200,7 +201,7 @@ class TextEmbedder(object):
         '''
         # for now not allowing this function without loading idf
         if self.trained and self.business_idf and self.user_idf:
-            tf = augmented_embed_sent(text, alpha, minimum_probability)
+            tf = self.augmented_embed_text(text, alpha, minimum_probability)
             bidf = self.business_idf_dict[business_id]
             uidf = self.user_idf_dict[user_id]
             out = np.multiply(np.multiply(tf, uidf), bidf)
@@ -216,18 +217,26 @@ class TextEmbedder(object):
 if __name__ == '__main__':
     dictionary = corpora.Dictionary.load('../workspace/gensim/chinsese_dict.dict')
     model =  models.LdaModel.load('../workspace/gensim/lda.model')
-    model = TextEmbedder(model = model, dictionary = dictionary)
[…]

### 2017-11-13 topic_over_time/workspace/text_embedder.py
implemented embedding wrapper

@@ -221,8 +221,11 @@ if __name__ == '__main__':
     with open('u_idf.pickle', 'rb') as f:
         uidf_data = pickle.load(f)
 
+    with open('b_idf.pickle', 'rb') as f:
+        bidf_data = pickle.load(f)
 
-    model = TextEmbedder(model = model, dictionary = dictionary, user_idf = uidf_data)
+
+    model = TextEmbedder(model = model, dictionary = dictionary, user_idf = uidf_data, business_idf = bidf_data)
 
     user1 = 'CxDOIDnH8gp9KXzpBHJYXw'
     business = 'gtcsOodbmk4E0TulYHnlHA'
@@ -240,3 +243,5 @@ if __name__ == '__main__':
 
     print (model.augmented_embed_text(sample))
     print (model.user_tfidf_embed(sample, user1))
+    print (model.user_tf_business_idf(sample, business))
+    print (model.user_tfidf_business_idf(sample, user1, business))

### 2017-11-14 topic_over_time/lda_embedder/text_embedder.py
clean up

@@ -1,0 +1,247 @@
+'''
+Topic-based Text embedding class for Round 10 Yelp Dataset Challenge
+'''
+
+import pandas as pd
+import gensim
+from gensim.utils import simple_preprocess
+from gensim import corpora, models, similarities
+from gensim.parsing.preprocessing import STOPWORDS
+import nltk
+import numpy as np
+import pickle
+
+class TextEmbedder(object):
+    def __init__(self, **kwargs):
+        self.trained = True
+        self.business_idf = False
+        self.user_idf = False
+        if kwargs != None:
+            # load dictionary if exists
+            if 'dictionary' not in kwargs.keys():
+                self.dictionary = None
+                self.trained = False
+            else:
+                self.dictionary = kwargs['dictionary']
+
+            # load topic model if exists
+            if 'model' not in kwargs.keys():
+                self.model = None
+                self.trained = False
+            else:
+                self.model = kwargs['model']
+
+            # load user_idf if exists
+            if 'user_idf' not in kwargs.keys():
+                self.user_idf_dict = None
+            else:
+                self.user_idf_dict = kwargs['user_idf']
+                self.user_idf = True
+
+            # load user_idf if exists
+            if 'business_idf' not in kwargs.keys():
+                self.business_idf_dict = None
+            else:
+                self.business_idf_dict = kwargs['business_idf']
+                self.business_idf = True
+
+
+    def tokenize_(self, text):
+        '''
+        tokenize the text using the utils from Gensim
+
+        Input:
+            text(str) : text that you want to tokenize
+        Output
+            (list): tokenized text
+        '''
+        return [token for token in simple_preprocess(text) if token not in STOPWORDS]
+
+    def embed(self, text, minimum_probability = None):
+        '''
+        embed the raw text into the vector with the length of topic number
+
+        Input:
+            text(str) : text that you want to embed
+        Output:
+            (list): embedded text
+        '''
+        if self.trained:
+            model = self.model
+            dictionary = self.dictionary
+            text = self.tokenize_(text)
+            bow = self.dictionary.doc2bow(text)
+            kindex = self.model.get_document_topics(bow, minimum_probability)
+            out = [0.] * self.model.num_topics
+            for i, p in kindex:
+                out[i] = p
+            return np.array(out)
+        else:
+            print ('Load LDA model and dictionary')
+            return None
+
+
[…]

### 2017-11-14 topic_over_time/workspace/neural_net.py

@@ -49,6 +49,9 @@ def one_hot_three(stars):
 
 
 def layer(input_data, size_in, size_out, name):
+    '''
+    Implement tensor
+    '''
     with tf.name_scope(name):
         # weight as random normal variables
         w = tf.Variable(tf.random_normal([size_in, size_out]), name = 'W')
@@ -65,6 +68,9 @@ def layer(input_data, size_in, size_out, name):
 
 
 def output_layer(input_data, size_in, size_out, name):
+    '''
+    output tensor
+    '''
     with tf.name_scope(name):
         # weight as random normal variables
         w = tf.Variable(tf.random_normal([size_in, size_out]), name = 'W')
@@ -81,8 +87,34 @@ def output_layer(input_data, size_in, size_out, name):
 
 
 def build_model(x, input_size, hidden, out_size):
+    '''
+    implement a fully connected model
+    '''
     prev = input_size
     activation = x
+    # build a series of hidden layers
+    for name,i in enumerate(hidden):
+        activation = layer(activation, prev, i, 'hiddenlayer-'+str(name))
+        prev = i
+
+    # build an output layer
+    embedding_in = activation
+    out = output_layer(activation, hidden[-1], out_size, 'output')
+
+    return out, embedding_in
+
+def build_model_with_gate(x, gate_dimention ,input_size, hidden, out_size):
+    '''
+    implement a filter gate before input
+    '''
+    # implement random filter here
+    gate = np.zeros(input_size)
+    i = random.sample(set(np.arange(input_size)), gate_dimention)
+    gate[[i]] = 1.0
+
+    prev = input_size
+    activation = tf.multiply(x, gate)
+
     # build a series of hidden layers
     for name,i in enumerate(hidden):
         activation = layer(activation, prev, i, 'hiddenlayer-'+str(name))
@@ -105,23 +137,23 @@ if __name__ == '__main__':
     model = Gensimembedder(model = lda, dictionary = dictionary)
 
     case_review = reviews[reviews['business_id'] == 'yfxDa8RFOvJPQh0rNtakHA']
-    id_train, id_test, star_train, star_test = train_test_split(case_review['review_id'], case_review['stars'], test_size=0.33)
+    id_train, id_test, star_train, star_test = train_test_split(case_review['review_id'], case_review['stars'], test_size=0.2)
 
[…]

### 2017-11-18 latent_variable/Workspace/pyversion_train.py
s

@@ -1,0 +1,141 @@
+import pandas as pd
+import numpy as np
+from nltk.corpus import stopwords
+import seaborn as sns
+import json
+import matplotlib.pyplot as plt
+from gensim import corpora, models
+import pickle
+
+with open('rest_review.pickle', 'rb') as f:
+	rest_review = pickle.load(f)
+
+#preprocess
+from nltk.tokenize import RegexpTokenizer
+tokenizer = RegexpTokenizer(r'\w+')
+
+from nltk.corpus import stopwords
+en_stop = stopwords.words('english')
+
+from nltk.stem.porter import PorterStemmer
+p_stemmer = PorterStemmer()
+
+def preprocess(text):
+    raw = text.lower()
+    tokens = tokenizer.tokenize(raw)
+    
+    pospeech=[]
+    tag = nltk.pos_tag(tokens)
+    for j in tag:
+        if j[1] == 'NN' or j[1] == 'JJ':
+            pospeech.append(j[0])
+    # remove stop words from tokens
+    stopped_tokens = [i for i in pospeech if not i in en_stop]
+    
+    # stem tokens
+    stemmed_tokens = [p_stemmer.stem(i) for i in stopped_tokens]
+    
+    # add tokens to list
+    return stemmed_tokens
+
+NUM_TOPICS = 120
+from gensim import corpora, models
+
+
+def getlda(df):
+    texts = []
+    for i in df['text']:
+        texts.append(preprocess(i))
+    # turn our tokenized documents into a id <-> term dictionary
+    dictionary = corpora.Dictionary(texts)
+    # convert tokenized documents into a document-term matrix
+    corpus = [dictionary.doc2bow(text) for text in texts]
+    # generate LDA model
+    ldamodel = models.ldamodel.LdaModel(corpus, num_topics=NUM_TOPICS, id2word = dictionary, passes=20)
+    return ldamodel
+
+def getprefer(userid, ldamodel, df):
+    user_reviews = df.loc[df['user_id'] == userid]
+    l = np.zeros(NUM_TOPICS)
+    texts = []
+    for t in user_reviews['text']:
+        texts.append(preprocess(t))
+    
+    for i in ldamodel.get_document_topics(corpus):
+        for topic in i:
+            l[topic[0]] += topic[1]
+    topic_likelihood = []
+    for i in l:
+        topic_likelihood.append(i/sum(l))
+    return topic_likelihood
+
+
[…]

### 2017-11-18 latent_variable/Workspace/pyversion_train.py
123

@@ -7,9 +7,8 @@ import matplotlib.pyplot as plt
 from gensim import corpora, models
 import pickle
 
-with open('rest_review.pickle', 'rb') as f:
-	rest_review = pickle.load(f)
-
+rest_review = pd.read_csv('rest_review.csv')
+print (rest_review)
 #preprocess
 from nltk.tokenize import RegexpTokenizer
 tokenizer = RegexpTokenizer(r'\w+')
@@ -129,13 +128,10 @@ with open('lda.pickle', 'wb') as handle:
     pickle.dump(lda, handle, protocol=pickle.HIGHEST_PROTOCOL)
 
 groupby_user = rest_review.groupby('user_id').size().reset_index(name='counts')
-with open('groupby_user.pickle', 'wb') as handle:
-    pickle.dump(groupby_user, handle, protocol=pickle.HIGHEST_PROTOCOL)
+groupby_user.to_csv()
 
-perfer_added = add_prefer_to_df(rest_review, lda, groupby_user)
-with open('perfer_added.pickle', 'wb') as handle:
-    pickle.dump(perfer_added, handle, protocol=pickle.HIGHEST_PROTOCOL)
+prefer_added = add_prefer_to_df(rest_review, lda, groupby_user)
+prefer_added.to_csv()
 
 subscore_added = add_subscore_to_df(prefer_added, lda, group)
-with open('subscore.pickle', 'wb') as handle:
-    pickle.dump(subscore_added, handle, protocol=pickle.HIGHEST_PROTOCOL)
+subscore_added.to_csv()

### 2017-11-18 dl-style-transfer/load_vec.py
Loaded files to load in and create word embeddings

@@ -1,0 +1,21 @@
+import ast
+import numpy as np
+
+lib = {}
+
+with open("vocab.txt") as file:
+    for (i, l) in enumerate(file):
+        lib[l] = i
+
+def load_vecs():
+    acc = []
+    with open("vec.txt") as file:
+        for l in file:
+            line = l.split("=>")
+            acc.append({'text': line[0], 'vec': ast.literal_eval(line[1])})
+    return acc
+
+def word_to_one_hot(s):
+    ret = np.zeros(len(lib))
+    ret[lib[s]] = 1
+    return ret

### 2017-11-18 dl-style-transfer/make_gutenberg_json.py

@@ -50,4 +50,6 @@ for b in books:
     print(frame.shape)
     frames.append(frame.iloc[1:, :])
 
-pd.concat(frames).reset_index().to_json("./text_sentences.json")
+frame = pd.concat(frames)
+frame = frame.reset_index()
+frame.to_json("./text_sentences.json", orient="records")

### 2017-11-19 latent_variable/Workspace/pyversion_train.py
Las vegas

@@ -6,9 +6,35 @@ import json
 import matplotlib.pyplot as plt
 from gensim import corpora, models
 import pickle
+import nltk
 
+
+def load_json_to_df(datapass):
+    data = [] 
+    with open(datapass) as data_file: 
+        for f in data_file:
+            data.append(json.loads(f))
+    df = pd.DataFrame(data)
+    return df
+
+business = load_json_to_df("../../../dataset/business.json")
+review = load_json_to_df("../../../dataset/review.json")
+
+is_rest = []
+for i in business['categories']:
+    
+    if 'Restaurants' in i or 'Food' in i:
+        is_rest.append(True)
+    else:
+        is_rest.append(False)
+restaurants = business.loc[is_rest]
+
+rest_id = restaurants['business_id']
+rest_review = review.loc[review['business_id'].isin(rest_id)]
+'''
 rest_review = pd.read_csv('rest_review.csv')
 print (rest_review)
+'''
 #preprocess
 from nltk.tokenize import RegexpTokenizer
 tokenizer = RegexpTokenizer(r'\w+')

### 2017-11-19 dl-style-transfer/layers.py
Rewrote k layer, removed k-sparse

@@ -278,7 +278,7 @@ def xavier_initializer(shape, uniform=True, dtype=tf.float32, name='Xavier-Initi
         return tf.truncated_normal(shape, stddev=stddev, dtype=dtype, name=name)
 
 
-def k_sparse_transform(input_volume, k=2, method=1, name="K-Sparse"):
+def k_competitive_activation(input_volume, k=2, alpha = 0, epsilon=0.00001, name="K-Sparse"):
     """
     Takes an input volume and calculates the norm of each matrix along the feature axis. The top k of these
     are declared the "winners". The others lose and are set to zero.
@@ -291,51 +291,12 @@ def k_sparse_transform(input_volume, k=2, method=1, name="K-Sparse"):
     Returns:
         A tensor the same shape as input_volume with the top k matrices preserved and the rest set to zero
     """
-    # Calculate the norms for all Activation maps in the volume using method
-    norms = tf.norm(input_volume, ord=method, axis=(1, 2))
-    z = tf.zeros(tf.shape(input_volume))
-    # Get the top k indices
-    _, top = tf.nn.top_k(norms, k=k)
-    # Mask indices not in the top k
-    top_mask = [i in top for i in range(tf.shape(input_volume)[-1])]
-    # Set not top values to zero. Tile 1D mask to three dimensions
-    return tf.where(tf.tile(top_mask, tf.concat(tf.shape(input_volume)[:-1], [1])), input_volume, z, name=name)
-
-
-def k_competitive_activator(input_volume, alpha=0, k=2, method=1, name="K-Competitive"):
-    """
-    Takes an input volume and calculates the norm of each matrix along the feature axis. The top k of these
-    are declared the "winners". The others lose and are set to zero. An amplification term is added to the winners
-    proportional to alpha.
-
-    Args:
-        input_volume: The 3d tensor to be transformed
-        k: the number of winners to declare
-        alpha: Coefficient on the amplification term
-        method: the type of norm to calculate
-        name: the name of the returned tensor
-    Returns:
-        A tensor the same shape as input_volume with the top k matrices amplified and the rest set to zero
-    """
[…]

### 2017-11-19 dl-style-transfer/layers.py
Updated and commented k competitive layer

@@ -278,7 +278,7 @@ def xavier_initializer(shape, uniform=True, dtype=tf.float32, name='Xavier-Initi
         return tf.truncated_normal(shape, stddev=stddev, dtype=dtype, name=name)
 
 
-def k_competitive_activation(input_volume, k=2, alpha = 0, epsilon=0.00001, name="K-Sparse"):
+def k_competitive_activation(input_volume, phase_train, k=2, alpha = 0, epsilon=0.00001, name="K-Sparse"):
     """
     Takes an input volume and calculates the norm of each matrix along the feature axis. The top k of these
     are declared the "winners". The others lose and are set to zero.
@@ -291,12 +291,24 @@ def k_competitive_activation(input_volume, k=2, alpha = 0, epsilon=0.00001, name
     Returns:
         A tensor the same shape as input_volume with the top k matrices preserved and the rest set to zero
     """
-    shape = input_volume.shape.as_list()
-    ab = tf.abs(input_volume)
-    energy = tf.reduce_sum(ab, axis=-1)
-    _, ind = tf.nn.top_k(ab, k)
-    mask = tf.reduce_sum(tf.one_hot(ind, shape[-1], on_value=1.0, off_value=0.0, dtype=tf.float32), -2)
-    royale = input_volume * mask
-    unit = royale / (tf.abs(royale) + epsilon)
-    act = alpha * tf.expand_dims(energy, -1) * unit
-    return tf.add(royale, act, name=name), mask
+    def train():
+        # Get the shape and element-wise absolute value of the input volume
+        shape = input_volume.shape.as_list()
+        ab = tf.abs(input_volume)
+        # Calculate the base energy by taking the reduced sum of the feature dimension
+        energy = tf.reduce_sum(ab, axis=-1)
+        # Find the top k values in the feature dimension for each spatial dimension
+        _, ind = tf.nn.top_k(ab, k)
+        # Produce and apply a mask setting the losing values to zero
+        mask = tf.reduce_sum(tf.one_hot(ind, shape[-1], on_value=1.0, off_value=0.0, dtype=tf.float32), -2)
+        royale = input_volume * mask
+        # Get the unit positions of the masked input to get a tensor of ~ 1, 0, -1
+        unit = royale / (tf.abs(royale) + epsilon)
+        # Calculate and add the energy term
+        energy_term = alpha * tf.expand_dims(energy, -1) * unit
+        return royale + energy_term
+
+    def test():
[…]

### 2017-11-19 dl-style-transfer/layers.py
Updated doc string of layers.py

@@ -278,15 +278,17 @@ def xavier_initializer(shape, uniform=True, dtype=tf.float32, name='Xavier-Initi
         return tf.truncated_normal(shape, stddev=stddev, dtype=dtype, name=name)
 
 
-def k_competitive_activation(input_volume, phase_train, k=2, alpha = 0, epsilon=0.00001, name="K-Sparse"):
+def k_competitive_activation(input_volume, phase_train, k=2, alpha = 0, epsilon=0.00001, name="K-Competitive"):
     """
     Takes an input volume and calculates the norm of each matrix along the feature axis. The top k of these
     are declared the "winners". The others lose and are set to zero.
 
     Args:
         input_volume: The 3d tensor to be transformed
+        phase_train: A flag that tells the layer whether or not it is in the training phase
         k: the number of winners to declare
-        method: the type of norm to calculate
+        alpha: Sets the intensity of the energy parameter
+        epsilon: A small number to perturb the divisor so to avoid dividing by zero
         name: the name of the returned tensor
     Returns:
         A tensor the same shape as input_volume with the top k matrices preserved and the rest set to zero

### 2017-11-19 dl-style-transfer/layers.py
Made KATE autoencoder

@@ -1,316 +1,0 @@
-from __future__ import print_function
-from __future__ import division
-from __future__ import absolute_import
-
-import tensorflow as tf
-import numpy as np
-import math
-
-
-def batch_norm(input, phase_train, decay=0.9, custom_inits=None, scope='BN'):
-    """Creates a batch normalization layer.
-
-    Used to stabilize distribution of outputs from a layer. Typically used right before a non-linearity. Works on
-    n-dimensional data.
-
-    Ref.: http://stackoverflow.com/questions/33949786/how-could-i-use-batch-normalization-in-tensorflow
-    Ref.: https://arxiv.org/pdf/1502.03167.pdf
-
-    Args:
-        input:         Tensor,  shaped [batch, features...] allowing it do be used with Conv or FC layers of any shape.
-        phase_train:   Boolean tensor, true indicates training phase.
-        decay:         Float. The decay to use for the exponential moving average.
-        custom_inits:  Dict from strings to functions that take a shape and return a tensor. These functions
-                       are used to initialize the corresponding variable. If a variable is not in the dict, then it is
-                       initialized with the default initializer for that variable. If None, then default initial
-        scope:         String or VariableScope to use as the variable scope.
-    Returns:
-        normed, vars:  `normed` is a tensor of the batch-normalized features, and has same shape as `input`.
-                       `vars` is a dict of the variables.
-    """
-    x_shape = input.shape.as_list()  # Don't deal with a TensorShape and instead use a list
-
-    # Check to ensure the minimum shape is met and there are no unknown dims in important places
-    if None in x_shape[1:] or len(x_shape) < 2:
-        raise ValueError("`input.shape` must be [batch, ..., features].")
-
-    with tf.variable_scope(scope):
-        # Define default initializers for beta and gamma. These are functions from shape to tensor.
-        inits = {
-            'Beta': lambda shape: tf.constant(0., shape=shape),
-            'Gamma': lambda shape: tf.constant(1., shape=shape),
-        }
-        if custom_inits is not None:
-            inits.update(custom_inits)  # Overwrite default inits with `custom_inits`
-
-        beta = tf.get_variable('Beta', initializer=inits['Beta']([x_shape[-1]]))  # Learned mean
-        gamma = tf.get_variable('Gamma', initializer=inits['Gamma']([x_shape[-1]]))  # Learned std. dev.
-
-        # Get mean and variance over batch and spatial dims
[…]

### 2017-11-29 dl_style_transfer/workspace/kate_new.py
trained kate

@@ -87,7 +87,7 @@ class Kate:
             for i in range(0, training_size, batch_size):
                 idx = perm[i:i + batch_size]
                 x_batch = x_train[idx]
-                _, loss_val = self._sess.run([self._train_step, self._loss], feed_dict={self._x: x_batch})
+                _, loss_val = self._sess.run([self._train_step, self._loss], feed_dict={self._x: x_batch, self._phase_train: False})
                 current_time = time()
                 if progress_interval is not None and (current_time - last_time) >= progress_interval:
                     last_time = current_time

### 2017-12-01 dl_style_transfer/Train_Kate_embeds.py
Fixed some inconsistencies in git, moved model to saved folder

@@ -1,3 +1,7 @@
+import os
+import sys
+sys.path.append(os.path.abspath('../'))
+
 import dl_style_transfer.from_shake_yelp
 import dl_style_transfer.workspace.kate_new as k
 import numpy as np
@@ -7,5 +11,5 @@ x_train = dl_style_transfer.from_shake_yelp.get_ryans_strange_input()
 kate = k.Kate(128, dl_style_transfer.from_shake_yelp.vocab_length(), 32, 6.26)
 kate.train(x_train, 100, 32)
 
+kate.save_model("saved/Saved_Kate.ckpt")
 
-kate.save_model("./Saved_Kate.mod")

### 2017-12-01 dl_style_transfer/Train_Kate_embeds.py
Made notebook for exploring quality of embeddings generated by KATE

@@ -1,14 +1,14 @@
+import numpy as np
 import os
 import sys
 sys.path.append(os.path.abspath('../'))
 
-import dl_style_transfer.from_shake_yelp
-import dl_style_transfer.workspace.kate_new as k
-import numpy as np
+import dl_style_transfer.from_shake_yelp as yelp
+from dl_style_transfer.workspace.kate_new import Kate
 
 
-x_train = dl_style_transfer.from_shake_yelp.get_ryans_strange_input()
-kate = k.Kate(128, dl_style_transfer.from_shake_yelp.vocab_length(), 32, 6.26)
+x_train = yelp.get_ryans_strange_input()
+kate = Kate(128, yelp.vocab_length(), 32, 6.26)
 kate.train(x_train, 100, 32)
 
 kate.save_model("saved/Saved_Kate.ckpt")

### 2017-12-01 dl_style_transfer/workspace/kate_new.py

@@ -29,15 +29,15 @@ class Kate:
             with tf.variable_scope('Encoder'):
                 fc1, var_dict = fc(hot, embedding_size, activation=tf.nn.tanh, scope='FC1')
 
-                k1 = k_comp(fc1, self._phase_train, k, alpha=alpha, scope='K-Comp1')
+                self._encoded = k_comp(fc1, self._phase_train, k, alpha=alpha, scope='Encoded')
 
             with tf.variable_scope('Decoder'):
                 weights = tf.transpose(var_dict['Weights'])  # `[embedding_size, vocab_size]`
                 bias = tf.get_variable('Scores', initializer=xavier_initializer((vocab_size,)))
-                scores = tf.matmul(k1, weights) + bias  # `[batch*max_seq_len, vocab_size]
+                scores = tf.matmul(self._encoded, weights) + bias  # `[batch*max_seq_len, vocab_size]
 
-                self._y_hat = tf.nn.softmax(scores, name='Y-Hat')
-                self._pred = tf.argmax(self._y_hat, axis=-1, name='Predicted')
+                self._decoded = tf.nn.softmax(scores, name='Decoded')
+                self._argmax = tf.argmax(self._decoded, axis=-1, name='Decoded-Argmax')
 
             with tf.variable_scope('Loss'):
                 self._loss = tf.reduce_mean(tf.nn.sparse_softmax_cross_entropy_with_logits(logits=scores, labels=self._x, name='Loss'))
@@ -97,18 +97,35 @@ class Kate:
             print("Completed Training.")
         return loss_val
 
-    def apply(self, x_data):
-        """Applies the model to the batch of data provided. Typically called after the model is trained.
+    def encode(self, raw_data):
+        """Encodes the batch of data provided. Typically called after the model is trained.
 
         Args:
-            x_data: A numpy ndarray of the data to apply the model to. Should have the same shape as the training data,
-                    e.g. `[batch_size]`.
+            raw_data: A numpy ndarray of the data to encode. Should have shape `[batch_size]`.
 
         Returns:
             A numpy ndarray of the data, with shape `[batch_size, embedding_size]`
         """
         with self._sess.as_default():
-            return self._sess.run(self._y_hat, feed_dict={self._x: x_data, self._phase_train: False})
+            return self._sess.run(self._encoded, feed_dict={self._x: raw_data, self._phase_train: False})
+
+    def decode(self, encodings, do_argmax=True):
+        """Decodes the batch of data provided. Typically called after the model is trained.
+
+        Args:
[…]

### 2017-12-02 dl_style_transfer/from_shake_yelp.py
Fixed errors with ryans_strange_input
get_bag takes a LOT of memory, use is not advised

@@ -4,48 +4,48 @@ import os
 
 here = os.path.dirname(os.path.abspath(__file__))
 
-yelp = list(open(os.path.join(here, 'yelp_sentences.txt')))
-shake = list(open(os.path.join(here, 'shake_sentences.txt')))
+sents = list(open(os.path.join(here, 'yelp_sentences.txt'))) + list(open(os.path.join(here, 'shake_sentences.txt')))
 
+thresh = 5
 
 col = dict()
 word_to_ind = dict()
 ind_to_word = dict()
 
+
 def __line_into_col__(line):
-    tokens = dl_style_transfer.workspace.data_helpers.clean_str(line)
+    tokens = dl_style_transfer.workspace.data_helpers.clean_str(line).split(" ")
     for wor in tokens:
         if col.get(wor) is None:
             col[wor] = 1
         else:
             col[wor] = col[wor] + 1
 
-for l1, l2 in zip(yelp, shake):
-    __line_into_col__(l1)
-    __line_into_col__(l2)
+
+for l in sents:
+    __line_into_col__(l)
 
 lis = list(col.items())
 lis.sort(key=lambda count: count[1], reverse=True)
-for i, word in enumerate(col):
-    word_to_ind[word] = i
-    ind_to_word[i] = word
+for i, word in enumerate(lis):
+    word_to_ind[word[0]] = i
+    ind_to_word[i] = word[0]
 
 voc_len = len(word_to_ind)
 
+shape = (len(sents), voc_len)
+
 
 def get_bag():
-    bag = np.zeros((len(shake) + len(yelp), voc_len))
-    for j,sent in enumerate(shake):
-        for wor in dl_style_transfer.workspace.data_helpers.clean_str(sent):
+    bag = np.zeros(shape)
+    for j,sent in enumerate(sents):
+        for wor in dl_style_transfer.workspace.data_helpers.clean_str(sent).split(" "):
             bag[j, word_to_ind[wor]] = bag[j, word_to_ind[wor]] + 1
-    for j,sent in enumerate(yelp):
-        for wor in dl_style_transfer.workspace.data_helpers.clean_str(sent):
-            bag[j, word_to_ind[wor]] = bag[j, word_to_ind[wor]] + 1
-    return bag
+    return np.log(1 + bag) / np.max(np.log(1 + bag), axis=0)
 
 
 def string_to_vec(string):
-    tokens = dl_style_transfer.workspace.data_helpers.clean_str(string)
[…]

### 2017-12-02 dl_style_transfer/Train_Kate_embeds.py
Added seed to kate trainer

@@ -6,10 +6,11 @@ sys.path.append(os.path.abspath('../'))
 import dl_style_transfer.from_shake_yelp as yelp
 from dl_style_transfer.workspace.kate_new import Kate
 
+seed = 1337
+np.random.seed(seed)
 
 x_train = yelp.get_ryans_strange_input()
 kate = Kate(128, yelp.vocab_length(), 32, 6.26)
 kate.train(x_train, 100, 32)
 
-kate.save_model("saved/Saved_Kate.ckpt")
-
+kate.save_model("saved/kate_hot.ckpt")

### 2017-12-02 dl_style_transfer/Train_Kate_embeds.py
Added reconstruct method in kate and accuracy testing

@@ -4,13 +4,28 @@ import sys
 sys.path.append(os.path.abspath('../'))
 
 import dl_style_transfer.from_shake_yelp as yelp
+
 from dl_style_transfer.workspace.kate_new import Kate
+from sklearn.model_selection import train_test_split
 
 seed = 1337
 np.random.seed(seed)
 
-x_train = yelp.get_ryans_strange_input()
+dataset = yelp.get_ryans_strange_input()
+train, test = train_test_split(dataset)
 kate = Kate(128, yelp.vocab_length(), 32, 6.26)
-kate.train(x_train, 100, 32)
+#kate.train(train, 100, 32)
+#kate.save_model("saved/kate_hot.ckpt")
 
-kate.save_model("saved/kate_hot.ckpt")
+
+def random_sample(data, num_samples):
+    """Samples along first dimension of `data`"""
+    idxs = np.random.choice(data.shape[0], size=num_samples, replace=False)
+    return data[idxs]
+
+# TODO: Write code to batch when reconstructing, right now its not batching
+
+train_result = kate.reconstruct(train)
+test_result = kate.reconstruct(test)
+print("Training Accuracy:", np.mean(train_result == train))
+print("Testing Accuracy:", np.mean(test_result == test))

### 2017-12-02 dl_style_transfer/workspace/kate_new.py

@@ -113,7 +113,7 @@ class Kate:
         """Decodes the batch of data provided. Typically called after the model is trained.
 
         Args:
-            encodings:    A numpy ndarray of the data to decode. Should have shape `[batch_size, embedding_size]`.
+            encodings: A numpy ndarray of the data to decode. Should have shape `[batch_size, embedding_size]`.
             do_argmax: Whether or not to argmax the vectors returned to predict the word.
 
         Returns:
@@ -126,6 +126,25 @@ class Kate:
             return self._sess.run(
                 self._argmax if do_argmax else self._decoded,
                 feed_dict={self._encoded: encodings, self._phase_train: False})
+
+    def reconstruct(self, raw_data, do_argmax=True):
+        """Reconstructs the batch of data provided by encoding and then decoding it. Typically called after the model
+        is trained.
+
+        Args:
+            raw_data:  A numpy ndarray of the data to reconstruct. Should have shape `[batch_size]`.
+            do_argmax: Whether or not to argmax the vectors returned to reconstruct the word.
+
+        Returns:
+            A numpy ndarray of the reconstructed data. If `do_argmax` is `False`, then the data will have shape
+            `[batch_size, vocab_size]` and will be populated by probabilities. If `do_argmax` is `True` the shape
+            is `[batch_size]` and the data will be populated by the indices of the reconstructed words in the vocabulary
+            that the model was trained on.
+        """
+        with self._sess.as_default():
+            return self._sess.run(
+                self._argmax if do_argmax else self._decoded,
+                feed_dict={self._x: raw_data, self._phase_train: False})
 
     def save_model(self, save_path=None):
         """Saves the model in the specified file.

### 2017-12-02 dl_style_transfer/Train_Kate_embeds.py
trained kate

@@ -14,8 +14,8 @@ np.random.seed(seed)
 dataset = yelp.get_ryans_strange_input()
 train, test = train_test_split(dataset)
 kate = Kate(128, yelp.vocab_length(), 32, 6.26)
-#kate.train(train, 100, 32)
-#kate.save_model("saved/kate_hot.ckpt")
+kate.train(train, 100, 128)
+kate.save_model("saved/kate_hot.ckpt")
 
 
 def random_sample(data, num_samples):

### 2017-12-02 dl_style_transfer/Train_Kate_embeds.py
Made KATE able to accept either [batch] or [batch,embedding] as input

@@ -14,7 +14,7 @@ np.random.seed(seed)
 
 dataset = yelp.get_ryans_strange_input()
 train, test = train_test_split(dataset)
-kate = Kate(128, yelp.vocab_length(), 32, 6.26, load_model='saved/100-epoch/kate-hot-100.ckpt')
+kate = Kate(yelp.vocab_length(), 128, 32, 6.26, load_model='saved/100-epoch/kate-hot-100.ckpt')
 # kate.train(train, 100, 128)
 # kate.save_model("saved/100-epoch/kate-hot-100.ckpt")
 
@@ -41,7 +41,7 @@ def compute_accuracy(data, batch_size, start_stop_info=True, progress_interval=5
         current_time = time()
         if progress_interval is not None and (current_time - last_time) >= progress_interval:
             last_time = current_time
-            print("Computing accuracy. Percent complete:", 100*count/n_batches, i)
+            print("Computing accuracy. Percent complete:", 100*count/n_batches)
         count += 1
 
     if start_stop_info:

### 2017-12-02 dl_style_transfer/workspace/kate_new.py

@@ -13,8 +13,20 @@ from time import time, strftime
 
 class Kate:
 
-    def __init__(self, embedding_size, vocab_size, k, alpha, learning_rate=0.001, load_model=None):
-        self._vocab_size = vocab_size
+    def __init__(self, embedding_size_in, embedding_size_out, k, alpha, learning_rate=0.001, load_model=None):
+        """Initializes the KATE model. Does not perform any training.
+
+        Args:
+            embedding_size_in:  The size of the input embeddings. For word embeddings, this is the vocabulary size.
+            embedding_size_out: The size of the output embeddings. This is the size of the encoded vectors.
+            k:                  The number of neurons to keep in the k-competitive layer.
+            alpha:              Sets the intensity of the energy redistribution in the k-comptitive layer.
+            learning_rate:      The learning rate for training.
+            load_model:         A string giving the path to the model to load. If `None`, the model's weights are
+                                randomly initialized to start training from scratch.
+        """
+        self._embedding_size_in = embedding_size_in
+        self._embedding_size_out = embedding_size_out
         self._k = k
         self._alpha = alpha
 
@@ -24,17 +36,17 @@ class Kate:
             self._x = tf.placeholder(tf.int32, shape=[None], name='X')
             self._phase_train = tf.placeholder(tf.bool, name='Phase')
 
-            hot = tf.one_hot(self._x, depth=vocab_size, name='Hot')  # `[batch, vocab_size]`
+            self._embedding = tf.one_hot(self._x, depth=embedding_size_in, name='Embedding')  # `[batch, embedding_size_in]`
 
             with tf.variable_scope('Encoder'):
-                fc1, var_dict = fc(hot, embedding_size, activation=tf.nn.tanh, scope='FC1')
+                fc1, var_dict = fc(self._embedding, embedding_size_out, activation=tf.nn.tanh, scope='FC1')
 
                 self._encoded = k_comp(fc1, self._phase_train, k, alpha=alpha, scope='Encoded')
 
             with tf.variable_scope('Decoder'):
-                weights = tf.transpose(var_dict['Weights'])  # `[embedding_size, vocab_size]`
-                bias = tf.get_variable('Scores', initializer=xavier_initializer((vocab_size,)))
-                scores = tf.matmul(self._encoded, weights) + bias  # `[batch*max_seq_len, vocab_size]
+                weights = tf.transpose(var_dict['Weights'])  # `[embedding_size_out, embedding_size_in]`
[…]

### 2017-12-02 dl_style_transfer/workspace/kate_new.py
Made inference functions in KATE also allow passing raw embeddings

@@ -123,7 +123,8 @@ class Kate:
             A numpy ndarray of the data, with shape `[batch_size, embedding_size]`
         """
         with self._sess.as_default():
-            return self._sess.run(self._encoded, feed_dict={self._x: raw_data, self._phase_train: False})
+            key = [self._x if len(raw_data.shape) is 1 else self._embedding]  # Choose which tensor to feed to
+            return self._sess.run(self._encoded, feed_dict={key: raw_data, self._phase_train: False})
 
     def decode(self, encodings, do_argmax=True):
         """Decodes the batch of data provided. Typically called after the model is trained.
@@ -154,9 +155,10 @@ class Kate:
             `[batch_size, embedding_size_in]`. If `do_argmax` is `True` the shape is `[batch_size]`.
         """
         with self._sess.as_default():
+            key = [self._x if len(raw_data.shape) is 1 else self._embedding]  # Choose which tensor to feed to
             return self._sess.run(
                 self._argmax if do_argmax else self._decoded,
-                feed_dict={self._x: raw_data, self._phase_train: False})
+                feed_dict={key: raw_data, self._phase_train: False})
 
     def save_model(self, save_path=None):
         """Saves the model in the specified file.

### 2017-12-02 dl_style_transfer/workspace/shallowCNN_reconstruct.py
Making reconstruction in in progress

@@ -78,6 +78,7 @@ with tf.Graph().as_default():
     sess = tf.Session(config=session_conf)
     with sess.as_default():
         cnn = TextCNN(
+            False,
             sequence_length=x_train.shape[1],
             num_classes=y_train.shape[1],
             vocab_size=len(vocab_processor.vocabulary_),
@@ -92,34 +93,10 @@ with tf.Graph().as_default():
         grads_and_vars = optimizer.compute_gradients(cnn.loss)
         train_op = optimizer.apply_gradients(grads_and_vars, global_step=global_step)
 
-        # Keep track of gradient values and sparsity (optional)
-        grad_summaries = []
-        for g, v in grads_and_vars:
-            if g is not None:
-                grad_hist_summary = tf.summary.histogram("{}/grad/hist".format(v.name), g)
-                sparsity_summary = tf.summary.scalar("{}/grad/sparsity".format(v.name), tf.nn.zero_fraction(g))
-                grad_summaries.append(grad_hist_summary)
-                grad_summaries.append(sparsity_summary)
-        grad_summaries_merged = tf.summary.merge(grad_summaries)
-
         # Output directory for models and summaries
         timestamp = str(int(time.time()))
         out_dir = os.path.abspath(os.path.join(os.path.curdir, "runs", timestamp))
         print("Writing to {}\n".format(out_dir))
-
-        # Summaries for loss and accuracy
-        loss_summary = tf.summary.scalar("loss", cnn.loss)
-        acc_summary = tf.summary.scalar("accuracy", cnn.accuracy)
-
-        # Train Summaries
-        train_summary_op = tf.summary.merge([loss_summary, acc_summary, grad_summaries_merged])
-        train_summary_dir = os.path.join(out_dir, "summaries", "train")
-        train_summary_writer = tf.summary.FileWriter(train_summary_dir, sess.graph)
-
-        # Dev summaries
-        dev_summary_op = tf.summary.merge([loss_summary, acc_summary])
-        dev_summary_dir = os.path.join(out_dir, "summaries", "dev")
-        dev_summary_writer = tf.summary.FileWriter(dev_summary_dir, sess.graph)
 
         # Checkpoint directory. Tensorflow assumes this directory already exists so we need to create it
         checkpoint_dir = os.path.abspath(os.path.join(out_dir, "checkpoints"))
@@ -143,12 +120,11 @@ with tf.Graph().as_default():
               cnn.input_y: y_batch,
               cnn.dropout_keep_prob: FLAGS.dropout_keep_prob
[…]

### 2017-12-02 dl_style_transfer/workspace/shallowCNN_train_simplified.py

@@ -78,6 +78,7 @@ with tf.Graph().as_default():
     sess = tf.Session(config=session_conf)
     with sess.as_default():
         cnn = TextCNN(
+            True,
             sequence_length=x_train.shape[1],
             num_classes=y_train.shape[1],
             vocab_size=len(vocab_processor.vocabulary_),
@@ -92,34 +93,10 @@ with tf.Graph().as_default():
         grads_and_vars = optimizer.compute_gradients(cnn.loss)
         train_op = optimizer.apply_gradients(grads_and_vars, global_step=global_step)
 
-        # Keep track of gradient values and sparsity (optional)
-        grad_summaries = []
-        for g, v in grads_and_vars:
-            if g is not None:
-                grad_hist_summary = tf.summary.histogram("{}/grad/hist".format(v.name), g)
-                sparsity_summary = tf.summary.scalar("{}/grad/sparsity".format(v.name), tf.nn.zero_fraction(g))
-                grad_summaries.append(grad_hist_summary)
-                grad_summaries.append(sparsity_summary)
-        grad_summaries_merged = tf.summary.merge(grad_summaries)
-
         # Output directory for models and summaries
         timestamp = str(int(time.time()))
         out_dir = os.path.abspath(os.path.join(os.path.curdir, "runs", timestamp))
         print("Writing to {}\n".format(out_dir))
-
-        # Summaries for loss and accuracy
-        loss_summary = tf.summary.scalar("loss", cnn.loss)
-        acc_summary = tf.summary.scalar("accuracy", cnn.accuracy)
-
-        # Train Summaries
-        train_summary_op = tf.summary.merge([loss_summary, acc_summary, grad_summaries_merged])
-        train_summary_dir = os.path.join(out_dir, "summaries", "train")
-        train_summary_writer = tf.summary.FileWriter(train_summary_dir, sess.graph)
-
-        # Dev summaries
-        dev_summary_op = tf.summary.merge([loss_summary, acc_summary])
-        dev_summary_dir = os.path.join(out_dir, "summaries", "dev")
-        dev_summary_writer = tf.summary.FileWriter(dev_summary_dir, sess.graph)
 
         # Checkpoint directory. Tensorflow assumes this directory already exists so we need to create it
         checkpoint_dir = os.path.abspath(os.path.join(out_dir, "checkpoints"))
@@ -143,12 +120,11 @@ with tf.Graph().as_default():
               cnn.input_y: y_batch,
               cnn.dropout_keep_prob: FLAGS.dropout_keep_prob
[…]

### 2017-12-02 dl_style_transfer/workspace/shallowCNN_transfer.py

@@ -1,0 +1,89 @@
+import tensorflow as tf
+import numpy as np
+import sys
+import os
+sys.path.append(os.path.abspath('../'))
+from dl_style_transfer.layers.layers import xavier_initializer
+
+
+class TextCNN(object):
+    """
+    A CNN for text classification.
+    Uses an embedding layer, followed by a convolutional, max-pooling and softmax layer.
+    """
+    def __init__(
+      self, trainable, sequence_length, num_classes, vocab_size,
+      embedding_size, filter_sizes, num_filters, l2_reg_lambda=0.0):
+        self.trainable = trainable
+
+        # Placeholders for input, output and dropout
+        self.input_x = tf.get_variable("input_x", initializer=xavier_initializer(shape=[None, sequence_length]))
+        self.input_y = tf.get_variable("input_y", initializer=xavier_initializer(shape=[None, sequence_length]))
+        self.dropout_keep_prob = tf.placeholder(tf.float32, name="dropout_keep_prob")
+
+        # Keeping track of l2 regularization loss (optional)
+        l2_loss = tf.constant(0.0)
+
+        # Embedding layer
+        with tf.name_scope("embedding"):
+            self.W = tf.Variable(
+                tf.random_uniform([vocab_size, embedding_size], -1.0, 1.0),
+                name="W", trainable=trainable)
+            self.embedded_chars = tf.nn.embedding_lookup(self.W, self.input_x)
+            self.embedded_chars_expanded = tf.expand_dims(self.embedded_chars, -1)
+
+        # Create a convolution + maxpool layer for each filter size
+        pooled_outputs = []
+        for i, filter_size in enumerate(filter_sizes):
+            with tf.name_scope("conv-maxpool-%s" % filter_size):
+                # Convolution Layer
+                filter_shape = [filter_size, embedding_size, 1, num_filters]
+                W = tf.Variable(tf.truncated_normal(filter_shape, stddev=0.1), name="W", trainable=trainable)
+                b = tf.Variable(tf.constant(0.1, shape=[num_filters]), name="b", trainable=trainable)
+                conv = tf.nn.conv2d(
+                    self.embedded_chars_expanded,
+                    W,
+                    strides=[1, 1, 1, 1],
+                    padding="VALID",
+                    name="conv")
+                # Apply nonlinearity
+                h = tf.nn.relu(tf.nn.bias_add(conv, b), name="relu")
[…]

### 2017-12-02 dl_style_transfer/new_kate_embeds.py
Fixed camerons indents and pushed some other stuff in reconstruction

@@ -1,6 +1,7 @@
 import numpy as np
 import os
 import sys
+
 sys.path.append(os.path.abspath('../'))
 
 import dl_style_transfer.from_shake_yelp as yelp
@@ -12,13 +13,28 @@ from time import time
 seed = 1337
 np.random.seed(seed)
 
-data=get_small_bag()
+data = yelp.get_small_bag()
 train, test = train_test_split(data)
 kate = Kate(yelp.vocab_length(), 128, 32, 6.26)
 # kate.train(train, 100, 128)
 
+
+def train_batch(data, batch_size, epoch=100, start_stop_info=True, progress_interval=5):
+    n_batches = np.ceil(len(data) / batch_size)
+    for _ in range(epoch):
+        for i in range(0, len(data), batch_size):
+            batch = data[i:i + batch_size]
+            npbatch = np.zeros(len(batch), yelp.vocab_len())
+            for i in range(len(batch)):
+                for j in range(len(batch[i])):
+                    npbatch[i, j] += npbatch[i, j] + 1
+            npbatch = np.log(1 + npbatch) / np.max(np.log(1 + npbatch), axis=1)
+            kate.train(npbatch, 1, 128)
+
+
 train_batch(data, 128, 100)
 kate.save_model("saved/100-epoch/kate-bag-words-100.ckpt")
+
 
 def random_sample(data, num_samples):
     """Samples along first dimension of `data`"""
@@ -26,40 +42,28 @@ def random_sample(data, num_samples):
     return data[idxs]
 
 
-def train_batch(data, batch_size, epoch=100, start_stop_info=True, progress_interval=5):
-    n_batches = np.ceil(len(data)/batch_size)
-    for _ in range(epoch):
-	for i in range(0, len(data), batch_size):
-		batch = data[i:i+batch_size]
-		npbatch = np.zeros(len(batch), yelp.vocab_len())
-		for i in range(len(batch)):
-			for j i nrange(len(batch[i])):
-				npbatch[i, j] += npbatch[i, j] + 1
-		npbatch = np.log(1 + npbatch) / np.max(np.log(1 + npbatch), axis=1)
-		kate.train(npbatch, 1, 128)
-
 def compute_accuracy(data, batch_size, start_stop_info=True, progress_interval=5):
     if start_stop_info:
         print("Computing accuracy for dataset of size", data.shape[0])
 
-    n_batches = np.ceil(data.shape[0]/batch_size)
+    n_batches = np.ceil(data.shape[0] / batch_size)
 
     accuracy = 0
[…]

### 2017-12-02 dl_style_transfer/workspace/shallowCNN_train_simplified.py

@@ -5,7 +5,7 @@ import os
 import time
 import datetime
 import data_helpers
-from shallowCNN_transfer import TextCNN
+from shallowCNN import TextCNN
 from tensorflow.contrib import learn
 
 # Parameters
@@ -78,7 +78,6 @@ with tf.Graph().as_default():
     sess = tf.Session(config=session_conf)
     with sess.as_default():
         cnn = TextCNN(
-            True,
             sequence_length=x_train.shape[1],
             num_classes=y_train.shape[1],
             vocab_size=len(vocab_processor.vocabulary_),

### 2017-12-02 dl_style_transfer/workspace/shallowCNN_transfer.py

@@ -12,7 +12,7 @@ class TextCNN(object):
     Uses an embedding layer, followed by a convolutional, max-pooling and softmax layer.
     """
     def __init__(
-      self, trainable, sequence_length, num_classes, vocab_size,
+      self, sequence_length, num_classes, vocab_size,
       embedding_size, filter_sizes, num_filters, l2_reg_lambda=0.0):
         self.trainable = trainable
 

### 2017-12-02 dl_style_transfer/new_kate_embeds.py
Fixed bugs in new_kate_embeds.py

@@ -24,11 +24,11 @@ def train_batch(data, batch_size, epoch=100, start_stop_info=True, progress_inte
     for _ in range(epoch):
         for i in range(0, len(data), batch_size):
             batch = data[i:i + batch_size]
-            npbatch = np.zeros(len(batch), yelp.vocab_len())
+            npbatch = np.zeros((len(batch), yelp.vocab_length()))
             for i in range(len(batch)):
                 for j in range(len(batch[i])):
                     npbatch[i, j] += npbatch[i, j] + 1
-            npbatch = np.log(1 + npbatch) / np.max(np.log(1 + npbatch), axis=1)
+            npbatch = np.log(1 + npbatch) / np.expand_dims(np.max(np.log(1 + npbatch), axis=1), -1)
             kate.train(npbatch, 1, 128)
 
 
@@ -53,11 +53,11 @@ def compute_accuracy(data, batch_size, start_stop_info=True, progress_interval=5
     count = 0
     for i in range(0, len(data), batch_size):
         batch = data[i:i + batch_size]
-        npbatch = np.zeros(len(batch), yelp.vocab_len())
+        npbatch = np.zeros((len(batch), yelp.vocab_length()), dtype=np.float32)
         for i in range(len(batch)):
             for j in range(len(batch[i])):
                 npbatch[i, j] += npbatch[i, j] + 1
-        npbatch = np.log(1 + npbatch) / np.max(np.log(1 + npbatch), axis=1)
+        npbatch = np.log(1 + npbatch) / np.expand_dims(np.max(np.log(1 + npbatch), axis=1), -1)
         reconstructed = kate.reconstruct(npbatch)
         accuracy += np.sum(reconstructed == npbatch)
         current_time = time()

### 2017-12-02 dl_style_transfer/workspace/kate_new.py
Fixed list around key in KATE

@@ -89,7 +89,7 @@ class Kate:
         """
         training_size = x_train.shape[0]
 
-        key = [self._x if len(x_train.shape) is 1 else self._embedding]  # Choose which tensor to feed to based on shape
+        key = self._x if len(x_train.shape) is 1 else self._embedding  # Choose which tensor to feed to based on shape
 
         # Training loop for parameter tuning
         if start_stop_info:
@@ -123,7 +123,7 @@ class Kate:
             A numpy ndarray of the data, with shape `[batch_size, embedding_size]`
         """
         with self._sess.as_default():
-            key = [self._x if len(raw_data.shape) is 1 else self._embedding]  # Choose which tensor to feed to
+            key = self._x if len(raw_data.shape) is 1 else self._embedding  # Choose which tensor to feed to
             return self._sess.run(self._encoded, feed_dict={key: raw_data, self._phase_train: False})
 
     def decode(self, encodings, do_argmax=True):
@@ -155,7 +155,7 @@ class Kate:
             `[batch_size, embedding_size_in]`. If `do_argmax` is `True` the shape is `[batch_size]`.
         """
         with self._sess.as_default():
-            key = [self._x if len(raw_data.shape) is 1 else self._embedding]  # Choose which tensor to feed to
+            key = self._x if len(raw_data.shape) is 1 else self._embedding  # Choose which tensor to feed to
             return self._sess.run(
                 self._argmax if do_argmax else self._decoded,
                 feed_dict={key: raw_data, self._phase_train: False})

### 2017-12-02 dl_style_transfer/workspace/shallowCNN_transfer.py

@@ -12,13 +12,11 @@ class TextCNN(object):
     Uses an embedding layer, followed by a convolutional, max-pooling and softmax layer.
     """
     def __init__(
-      self, sequence_length, num_classes, vocab_size,
+      self, num_reconstructions, sequence_length, num_classes, vocab_size,
       embedding_size, filter_sizes, num_filters, l2_reg_lambda=0.0):
-        self.trainable = trainable
 
         # Placeholders for input, output and dropout
-        self.input_x = tf.get_variable("input_x", initializer=xavier_initializer(shape=[None, sequence_length]))
-        self.input_y = tf.get_variable("input_y", initializer=xavier_initializer(shape=[None, sequence_length]))
+        self.input_x = tf.get_variable("input_x", initializer=xavier_initializer(shape=[num_reconstructions, sequence_length]))
         self.dropout_keep_prob = tf.placeholder(tf.float32, name="dropout_keep_prob")
 
         # Keeping track of l2 regularization loss (optional)

### 2017-12-02 dl_style_transfer/new_kate_embeds.py
Made kate properly be able to select between one hot and bow model

@@ -15,7 +15,7 @@ np.random.seed(seed)
 
 data = yelp.get_small_bag()
 train, test = train_test_split(data)
-kate = Kate(yelp.vocab_length(), 128, 32, 6.26)
+kate = Kate(yelp.vocab_length(), 128, False, 32, 6.26)
 # kate.train(train, 100, 128)
 
 

### 2017-12-02 dl_style_transfer/workspace/kate_new.py

@@ -13,12 +13,15 @@ from time import time, strftime
 
 class Kate:
 
-    def __init__(self, embedding_size_in, embedding_size_out, k, alpha, learning_rate=0.001, load_model=None):
+    def __init__(self, embedding_size_in, embedding_size_out, expand_hot, k, alpha, learning_rate=0.001, load_model=None):
         """Initializes the KATE model. Does not perform any training.
-
+,
         Args:
-            embedding_size_in:  The size of the input embeddings. For word embeddings, this is the vocabulary size.
+            embedding_size_in:  The size of the input embeddings. If `expand_hot` is `True`, this is the size of the one
+                                hot vectors that will be generated.
             embedding_size_out: The size of the output embeddings. This is the size of the encoded vectors.
+            expand_hot:         Boolean determining if the input represents indices of a word list to be expanded using
+                                a one-hot representation.
             k:                  The number of neurons to keep in the k-competitive layer.
             alpha:              Sets the intensity of the energy redistribution in the k-comptitive layer.
             learning_rate:      The learning rate for training.
@@ -33,10 +36,13 @@ class Kate:
         print("Constructing KATE architecture...")
         self._graph = tf.Graph()
         with self._graph.as_default():
-            self._x = tf.placeholder(tf.int32, shape=[None], name='X')
             self._phase_train = tf.placeholder(tf.bool, name='Phase')
 
-            self._embedding = tf.one_hot(self._x, depth=embedding_size_in, name='Embedding')  # `[batch, embedding_size_in]`
+            if expand_hot:
+                self._x = tf.placeholder(tf.int32, shape=[None], name='X')
+                self._embedding = tf.one_hot(self._x, depth=embedding_size_in, name='Embedding')  # `[batch, embedding_size_in]`
+            else:
+                self._embedding = tf.placeholder(tf.float32, shape=[None, embedding_size_in])
 
             with tf.variable_scope('Encoder'):
                 fc1, var_dict = fc(self._embedding, embedding_size_out, activation=tf.nn.tanh, scope='FC1')
@@ -52,7 +58,7 @@ class Kate:
                 self._argmax = tf.argmax(self._decoded, axis=-1, name='Decoded-Argmax')
 
             with tf.variable_scope('Loss'):
-                self._loss = tf.reduce_mean(tf.nn.sparse_softmax_cross_entropy_with_logits(logits=scores, labels=self._x, name='Loss'))
[…]

### 2017-12-02 dl_style_transfer/train_kate_embeds.py
Deleted defunct saved models, made KATE properly choose to `expand_hot`

@@ -14,9 +14,9 @@ np.random.seed(seed)
 
 dataset = yelp.get_ryans_strange_input()
 train, test = train_test_split(dataset)
-kate = Kate(yelp.vocab_length(), 128, 32, 6.26, load_model='saved/100-epoch/kate-hot-100.ckpt')
-# kate.train(train, 100, 128)
-# kate.save_model("saved/100-epoch/kate-hot-100.ckpt")
+kate = Kate(yelp.vocab_length(), 128, True, 32, 6.26)
+kate.train(train, 100, 128)
+kate.save_model("saved/100-epoch/kate-hot-100.ckpt")
 
 
 def random_sample(data, num_samples):

### 2017-12-02 dl_style_transfer/workspace/kate_new.py

@@ -30,6 +30,7 @@ class Kate:
         """
         self._embedding_size_in = embedding_size_in
         self._embedding_size_out = embedding_size_out
+        self._expand_hot = expand_hot
         self._k = k
         self._alpha = alpha
 
@@ -40,9 +41,9 @@ class Kate:
 
             if expand_hot:
                 self._x = tf.placeholder(tf.int32, shape=[None], name='X')
-                self._embedding = tf.one_hot(self._x, depth=embedding_size_in, name='Embedding')  # `[batch, embedding_size_in]`
+                self._embedding = tf.one_hot(self._x, depth=embedding_size_in, name='Embedding')
             else:
-                self._embedding = tf.placeholder(tf.float32, shape=[None, embedding_size_in])
+                self._embedding = tf.placeholder(tf.float32, shape=[None, embedding_size_in], name='Embedding')
 
             with tf.variable_scope('Encoder'):
                 fc1, var_dict = fc(self._embedding, embedding_size_out, activation=tf.nn.tanh, scope='FC1')
@@ -95,7 +96,10 @@ class Kate:
         """
         training_size = x_train.shape[0]
 
-        key = self._x if len(x_train.shape) is 1 else self._embedding  # Choose which tensor to feed to based on shape
+        if self._expand_hot:
+            key = self._x
+        else:
+            key = self._embedding
 
         # Training loop for parameter tuning
         if start_stop_info:
@@ -129,7 +133,10 @@ class Kate:
             A numpy ndarray of the data, with shape `[batch_size, embedding_size]`
         """
         with self._sess.as_default():
-            key = self._x if len(raw_data.shape) is 1 else self._embedding  # Choose which tensor to feed to
+            if len(raw_data.shape) is 1:
+                key = self._x
+            else:
+                key = self._embedding
             return self._sess.run(self._encoded, feed_dict={key: raw_data, self._phase_train: False})
 
     def decode(self, encodings, do_argmax=True):
@@ -161,7 +168,10 @@ class Kate:
             `[batch_size, embedding_size_in]`. If `do_argmax` is `True` the shape is `[batch_size]`.
         """
         with self._sess.as_default():
-            key = self._x if len(raw_data.shape) is 1 else self._embedding  # Choose which tensor to feed to
+            if len(raw_data.shape) is 1:
+                key = self._x
+            else:
+                key = self._embedding
             return self._sess.run(
                 self._argmax if do_argmax else self._decoded,
                 feed_dict={key: raw_data, self._phase_train: False})

### 2017-12-02 dl_style_transfer/paper/main.tex
Initial commit of paper

\documentclass{vldb}
\usepackage{graphicx}
\usepackage{balance}  % for  \balance command ON LAST PAGE  (only there!)
\usepackage[capposition=top]{floatrow}
\usepackage{float}
\usepackage[caption = false]{subfig}
\usepackage{wrapfig}

\begin{document}

% ****************** TITLE ****************************************

\title{On the Use of K-Competitive Networks \\ for Writing Style Transfer}

% ****************** AUTHORS **************************************

\numberofauthors{3}

\author{
\alignauthor
Luca Leeser\\
       \affaddr{Cornell University}\\
       \email{ll698@cornell.edu}
\alignauthor
Ryan Butler\\
       \affaddr{Cornell University}\\
       \email{rjb392@cornell.edu}
\and
\alignauthor 
Cameron Ibrahim\\
       \affaddr{Cornell University}\\
       \email{cai29@cornell.edu}
\alignauthor 
Yuji Akimoto\\
       \affaddr{Cornell University}\\
       \email{ya242@cornell.edu}
}

\date{1 December 2017}

\maketitle

\begin{abstract}
Writing style is a key component of the quality of any online review - a detailed and informative review is only useful insofar as it is able to retain a reader's attention. In this paper, we explore the use of $k$-competitive layers in convolutional neural networks to classify the author of a given piece of text. We then apply the techniques used in neural style transfer for images to transfer the writing style of one author onto the content written by another. Given sufficient examples of well-written reviews, our techniques can be used to globally improve the quality of reviews on Yelp.
\end{abstract}

% INTRODUCTION
\section{Introduction}
Neural style transfer \cite{GatysEB15a} has proven very successful at transferring the artistic style of an image onto the content of another. Due to the layered structure of convolutional neural networks, it was observed that later layers in the network produce feature representations of the content of an image, while the correlations between these features give a good representation of artistic style. More specifically, given a content image and style image, the algorithm treats the input to the network as a variable and simultaneously minimizes the $\ell_2$ norm between the input and content image's feature representations, and the input and style image's style representations.

\begin{figure}[h]
\subfloat{\includegraphics[width = .3\linewidth]{gates-hall.jpg}}
\hspace{0.1cm}
\subfloat{\includegraphics[width = .3\linewidth]{starry_night.jpg}}
\hspace{0.1cm}
\subfloat{\includegraphics[width = .3\linewidth]{gates-starry.png}}
\caption{\textmd{Cornell's Gates Hall stylized in the form of Vincent Van Gogh's \textit{Starry Night}.}}
\end{figure}

Modifications that optimize computational time \cite{JohnsonAL16}, preserve the texture of the style image \cite{GatysEB15}, and preserve facial structures in the content image \cite{KaurZD17}, among others, have further advanced the art of neural style transfer for images. However, applying similar techniques to text has proven difficult for a number of reasons. Firstly, textual data lives in an extremely sparse space, and therefore it is difficult to iteratively produce better stylized text while avoiding phrases that make no sense. Secondly, style and content are much more closely linked in text than they are in images - the same writer may write two passages of text in a completely different tone, yet maintain the same underlying style in a manner that is very subtle.

In this paper, we explore the use of $k$-competitive convolutional layers, a generalization of $k$-competitive layers designed for autoencoders in \cite{KATE}, which in turn are based on $k$-sparse layers as defined in \cite{MakhzaniF13}. These layers are integrated into a word-level convolutional neural network \cite{Kim14f}, and we perform a qualitative analysis on the quality of content and style representations generated by these networks.

% RELATED WORK
\section{Related Work}

% PRELIMINARY ANALYSIS
\section{Preliminary Analysis}
The majority of implementations of style transfer for images use the VGG-19 \cite{VGG19} architecture to generate content and style representations of an image. This network was originally trained to classify between 1000 images of the ImageNet challenge dataset \cite{ILSVRC15} and therefore is able to generate informative feature representations of a very large variety of objects. Given the resources required to train a similarly robust classifier for text, we first explore the tradeoffs of using an underlying network that is trained to discriminate between a much smaller number of classes by training a VGG network with the CIFAR-10 dataset \cite{Krizhevsky09} (here, we use pre-trained weights provided by \cite{Liu15}). Although this modified network is far less generalizable in terms of classification, we found that the content representations provided by later layers of the network were still informative enough to reconstruct the original image, even for images containing objects not included in the 10 classes of CIFAR-10.

% MODEL
\section{Model}
\subsection{Convolutional Neural Networks for Text Classification}
As the baseline for our comparisons we use a word-level convolutional neural network as designed by Yoon Kim in \cite{Kim14f}.

\begin{figure}[h]
\includegraphics[width=\linewidth]{cnn.png}
\caption{\textmd{Structure of the baseline convolutional neural network model.}}
\end{figure}

\subsection{K-Competitive Convolutional Layers}
It has been observed that encouraging sparsity when learning representations acts as a capable reguarlizer that improves performance on classification tasks. In \cite{MakhzaniF13}, Makhzani and Frey designed the $k$-sparse autoencoder and demonstrated its effectiveness as a preprocessing step on image data. In the feedforward phase, sparsity is used as the sole non-linearity: after computing the activations $z = W^Tx + b$, only the largest $k$ entries of $z$ are kept and the rest are set to 0.

Since textual data often has high-dimensionality, sparsity, and power-law distributions \cite{KATE}, autoencoders for text have often learned trivial features such as proper nouns specific to a certain passage. Chen and Zaki made a modification to $k$-sparse layers by introducing competition in the place of truncation: after computing the activations $z = tanh(W^Tx + b)$, only the $k$ entries with the largest absolute value are kept non-zero. These $k$ most ``competitive'' neurons are then augmented (with an amplification constant) with the \textbf{energy} of the ``losers'' that were made inactive, where the energy of a subset of neurons $H$ is defined as $\sum_{h_i \in H} |z_i|$.

\begin{figure}[h]
\centering
\includegraphics[width=.8\linewidth]{k_complayer.png}
\caption{\textmd{A fully connected $k$-competitive layer.}}
\end{figure}

Here, we propose a generalization of $k$-competitive layers to convolutional layers.

% EXPERIMENTS
\section{Experiments}
\subsection{Datasets and Processing}
Cite NLTK

\subsection{Hyperparameters and Training}

\subsection{Comparison of Architectures}

% RESULTS
\section{Results}

% CONCLUSION
\section{Conclusion}

% FURTHER DISCUSSION
\section{Future Extensions}

% ACKNOWLEDGMENTS 
\section{Acknowledgments}
The authors would like to thank Professor Thorsten Joachims at the department of Computer Science at Cornell University for his guidance, and their fellow members of the Cornell Data Science NLP Research Team for their support.

\bibliographystyle{abbrv}
\bibliography{sources.bib}

% APPENDIX
%pagebreak

\begin{appendix}
This is an appendix

\section{Graphs}

\end{appendix}
\end{document}

### 2017-12-02 dl_style_transfer/word2vec.py

@@ -17,4 +17,4 @@ if __name__ == "__main__":
     train_corpus = Corpus(os.getcwd())
     params = {'size': 200, 'window': 10, 'min_count': 10, 'workers': max(1, mp.cpu_count() - 1), 'sample': 1E-3, }
     model = gensim.models.Word2Vec(train_corpus, **params)
-    print(model.wv['liue'])
+    print(model.wv['live'])

### 2017-12-02 dl_style_transfer/paper/main.tex
Updated paper

@@
 \usepackage[caption = false]{subfig}
-\usepackage{wrapfig}
+%\usepackage{hyperref}
 
@@
 \alignauthor
+Yuji Akimoto\\
+       \affaddr{Cornell University}\\
+       \email{ya242@cornell.edu}
+\and
+\alignauthor 
 Ryan Butler\\
@@
        \email{rjb392@cornell.edu}
-\and
 \alignauthor 
@@
        \email{cai29@cornell.edu}
-\alignauthor 
-Yuji Akimoto\\
-       \affaddr{Cornell University}\\
-       \email{ya242@cornell.edu}
 }
@@
 The majority of implementations of style transfer for images use the VGG-19 \cite{VGG19} architecture to generate content and style representations of an image.
-This network was originally trained to classify between 1000 images of the ImageNet challenge dataset \cite{ILSVRC15} and therefore is able to generate informative feature representations of a very large variety of objects.
+This network was trained to classify between 1000 images of the ImageNet challenge dataset \cite{ILSVRC15} and therefore is able to generate informative feature representations of a very large variety of objects.
 Given the resources required to train a similarly robust classifier for text, we first explore the tradeoffs of using an underlying network that is trained to discriminate between a much smaller number of classes by training a VGG network with the CIFAR-10 dataset \cite{Krizhevsky09} (here, we use pre-trained weights provided by \cite{Liu15}).
@@
 \subsection{Convolutional Neural Networks for Text Classification}
+Although recurrent neural networks have proven adept at language recognition tasks, evaluating the overall content and style of written text is a task that is less dependent on sequential information, and a hidden state is likely too small to encode enough information for our purposes.
+We believe that a a convolutional neural network allows us to take advantage of the success of style transfer for images, in contrast to aforementioned approaches that treat style transfer as a machine translation problem.
+
 As the baseline for our comparisons we use a word-level convolutional neural network as designed by Yoon Kim in \cite{Kim14f}.
@@
 \section{Experiments}
-\subsection{Datasets and Processing}
-Cite NLTK
+\subsection{Datasets}
+We use the most prolific reviewers on Yelp\footnote{{\texttt{https://www.yelp.com/dataset/challenge}}} to generate a large amounts of text for various styles of writing.
+Although the reviews for a frequent user of Yelp may span a number of years, we make the assumption that a user's writing style remains constant over that period of time.
+This may not strictly be the case as language, particularly of the colloquial variety that is often found online, evolves over time and certain words serve as clear indicators of certain time periods.
+However, dealing with a time-varying vocabulary set is an extension that we have not yet considered.
+After identifying the most frequent reviewers, we tokenize all of their reviews using NLTK \cite{Loper02nltk:the} to generate a corpus.
 
@@
 \begin{appendix}
-This is an appendix
-
-\section{Graphs}
+%\href{https://github.com/CornellDataScience/Yelp-FA17/tree/master/dl_style_transfer}{Link} to Github repository for all code associated with this paper.
 

### 2017-12-02 dl_style_transfer/paper/main.tex
Updated paper

@@
 In this paper, we explore the use of $k$-competitive convolutional layers, a generalization of $k$-competitive layers designed for autoencoders in \cite{KATE}, which in turn are based on $k$-sparse layers as defined in \cite{MakhzaniF13}.
-These layers are integrated into a word-level convolutional neural network \cite{Kim14f}, and we perform a qualitative analysis on the quality of content and style representations generated by these networks.
+These layers are integrated into a word-level convolutional neural network \cite{Kim14f}, and we perform a qualitative analysis of the quality of content and style representations generated by these networks.
+A key benefit of our method is that it does not require a training set of translations between writing styles, which are very difficult to obtain.
 
@@
 \section{Related Work}
+Early methods at quantitatively determining the writing style of a piece of text focused on statistical analyses of the rates of passive and active sentences, the ratio of pronouns to nouns to adjectives, and the likelihood of adjacent words given their distribution in the English language.
+However, these methods rely on unreliable tokenizations and are difficult to adapt to style transfer.
+Xu et.
+al.
+\cite{Xu12} provided some of the first algorithmic style transfer methods between Shakespearean and modern English, but relied on a phrase table and did not take advantage of modern machine learning methods.
+
+Recent methods based on neural networks fall into two broad categories: those that treat the problem as a mono-linguistic machine translation problem, and those that attempt to generate style and content representations of text.
+\cite{Carlson17} and \cite{Jang16} fall under this first category, and generate stylized text that perform well according to BLEU score \cite{Papineni02}.
+However, these translation-based methods require a large dataset of tupled phrases that are identical in content and differ only in style.
+Use of passages in the Bible in \cite{Carlson17} and SparkNotes' Shakespearean translations in \cite{Jang16} present interesting but impractical test cases, while generating rap lyric translations with Google Translate via French \cite{Jang16} leaves much to be desired in terms of accuracy.
+
+\cite{Edirisooriya} and \cite{Kabbara16} both consider a similar method to ours in terms of generating style and content representations of text, and \cite{Kabbara16} defines three evaluation criteria: soundness (preservation of content), coherence (grammatical correctness \& common sense), and effectiveness (matches intended style).
+However, these lack sufficient experiments with which to evaluate the quality of their results.
 
@@
 The majority of implementations of style transfer for images use the VGG-19 \cite{VGG19} architecture to generate content and style representations of an image.
-This network was trained to classify between 1000 images of the ImageNet challenge dataset \cite{ILSVRC15} and therefore is able to generate informative feature representations of a very large variety of objects.
+This network was trained to classify images into one of the one thousand classes of the ImageNet challenge dataset \cite{ILSVRC15} and therefore is able to generate informative feature representations of a very large variety of objects.
 Given the resources required to train a similarly robust classifier for text, we first explore the tradeoffs of using an underlying network that is trained to discriminate between a much smaller number of classes by training a VGG network with the CIFAR-10 dataset \cite{Krizhevsky09} (here, we use pre-trained weights provided by \cite{Liu15}).
@@
 As the baseline for our comparisons we use a word-level convolutional neural network as designed by Yoon Kim in \cite{Kim14f}.
+A 1-d convolutional layer varies from those commonly found in architectures for image classification in that the receptive field of a filter is one-dimensional, and subsequent pooling layers operate along the time axis.
+The network takes as input a sentence, with each word encoded as a vector.
+As a ``shallow'' architecture, the network performs layer of convolution with filter lengths of 3, 4, 5 with 100 feature maps each, before a max-over-time pooling operation and a softmax layer.
 

### 2017-12-02 dl_style_transfer/paper/main.tex
Updated paper

@@
 We then apply the techniques used in neural style transfer for images to transfer the writing style of one author onto the content written by another.
-Given sufficient examples of well-written reviews, our techniques can be used to globally improve the quality of reviews on Yelp.
+Given sufficient examples of well-written reviews, our techniques can be used to improve the quality of reviews on online platforms such as Yelp or Amazon.
 \end{abstract}
@@
 However, these lack sufficient experiments with which to evaluate the quality of their results.
+\cite{Fu17} provides a quantitative assessment of their content and style representations, in addition to a more complex alternative architecture.
+All of the aforementioned works use a recurrent neural network encoder-decoder structure (otherwise referred to as a ``seq2seq'' model), with either a long short-term memory (LSTM) or gated recurrent unit (GRU) used as the underlying structure.
+These methods seek to encode the content of the input text into a low dimensional space, and then use the decoder to generate text in a specified style.
+Our key contribution is in the use of convolutional neural networks, which have proven very successful at tasks such as sentiment analysis \cite{Kim14f}.
 

### 2017-12-02 dl_style_transfer/workspace/shallowCNN.py
Made shallowcnn_transfer somewhat make sense

@@ -10,6 +10,13 @@ class TextCNN(object):
     def __init__(
       self, sequence_length, num_classes, vocab_size,
       embedding_size, filter_sizes, num_filters, l2_reg_lambda=0.0):
+        self.sequence_length = sequence_length
+        self.num_classes = num_classes
+        self.vocab_size = vocab_size
+        self.embedding_size = embedding_size
+        self.filter_sizes = filter_sizes
+        self.num_filters = num_filters
+        self.l2_reg_lambda = l2_reg_lambda
 
         # Placeholders for input, output and dropout
         self.input_x = tf.placeholder(tf.int32, [None, sequence_length], name="input_x")

### 2017-12-02 dl_style_transfer/workspace/shallowCNN_reconstruct.py

@@ -5,7 +5,7 @@ import os
 import time
 import datetime
 import data_helpers
-from shallowCNN_transfer import TextCNN
+from shallowCNN import TextCNN
 from tensorflow.contrib import learn
 
 # Parameters
@@ -78,7 +78,6 @@ with tf.Graph().as_default():
     sess = tf.Session(config=session_conf)
     with sess.as_default():
         cnn = TextCNN(
-            False,
             sequence_length=x_train.shape[1],
             num_classes=y_train.shape[1],
             vocab_size=len(vocab_processor.vocabulary_),
@@ -104,9 +103,6 @@ with tf.Graph().as_default():
         if not os.path.exists(checkpoint_dir):
             os.makedirs(checkpoint_dir)
         saver = tf.train.Saver(tf.global_variables(), max_to_keep=FLAGS.num_checkpoints)
-
-        # Write vocabulary
-        vocab_processor.save(os.path.join(out_dir, "vocab"))
 
         # Initialize all variables
         sess.run(tf.global_variables_initializer())

### 2017-12-02 dl_style_transfer/workspace/shallowCNN_transfer.py

@@ -12,11 +12,18 @@ class TextCNN(object):
     Uses an embedding layer, followed by a convolutional, max-pooling and softmax layer.
     """
     def __init__(
-      self, num_reconstructions, sequence_length, num_classes, vocab_size,
-      embedding_size, filter_sizes, num_filters, l2_reg_lambda=0.0):
+      self, num_reconstructions, trained_model):
+        self.num_reconstructions = num_reconstructions
+        self.sequence_length = trained_model.sequence_length
+        self.num_classes = trained_model.num_classes
+        self.vocab_size = trained_model.vocab_size
+        self.embedding_size = trained_model.embedding_size
+        self.filter_sizes = trained_model.filter_sizes
+        self.num_filters = trained_model.num_filters
+        self.l2_reg_lambda = trained_model.l2_reg_lambda
 
         # Placeholders for input, output and dropout
-        self.input_x = tf.get_variable("input_x", initializer=xavier_initializer(shape=[num_reconstructions, sequence_length]))
+        self.input_x = tf.get_variable("input_x", shape=[self.num_reconstructions, self.sequence_length], trainable=False)
         self.dropout_keep_prob = tf.placeholder(tf.float32, name="dropout_keep_prob")
 
         # Keeping track of l2 regularization loss (optional)
@@ -24,20 +31,19 @@ class TextCNN(object):
 
         # Embedding layer
         with tf.name_scope("embedding"):
-            self.W = tf.Variable(
-                tf.random_uniform([vocab_size, embedding_size], -1.0, 1.0),
-                name="W", trainable=trainable)
+            self.W = tf.get_variable(
+                name="W", trainable=False)
             self.embedded_chars = tf.nn.embedding_lookup(self.W, self.input_x)
             self.embedded_chars_expanded = tf.expand_dims(self.embedded_chars, -1)
 
         # Create a convolution + maxpool layer for each filter size
         pooled_outputs = []
-        for i, filter_size in enumerate(filter_sizes):
+        for i, filter_size in enumerate(self.filter_sizes):
             with tf.name_scope("conv-maxpool-%s" % filter_size):
                 # Convolution Layer
-                filter_shape = [filter_size, embedding_size, 1, num_filters]
-                W = tf.Variable(tf.truncated_normal(filter_shape, stddev=0.1), name="W", trainable=trainable)
[…]

### 2017-12-02 dl_style_transfer/workspace/shallowCNN.py
Changed shallowCNN to use tf.get_variable()

@@ -27,21 +27,19 @@ class TextCNN(object):
         l2_loss = tf.constant(0.0)
 
         # Embedding layer
-        with tf.name_scope("embedding"):
-            self.W = tf.Variable(
-                tf.random_uniform([vocab_size, embedding_size], -1.0, 1.0),
-                name="W")
+        with tf.variable_scope("embedding"):
+            self.W = tf.get_variable("W", initializer=tf.random_uniform([vocab_size, embedding_size], -1.0, 1.0))
             self.embedded_chars = tf.nn.embedding_lookup(self.W, self.input_x)
             self.embedded_chars_expanded = tf.expand_dims(self.embedded_chars, -1)
 
         # Create a convolution + maxpool layer for each filter size
         pooled_outputs = []
         for i, filter_size in enumerate(filter_sizes):
-            with tf.name_scope("conv-maxpool-%s" % filter_size):
+            with tf.variable_scope("conv-maxpool-%s" % filter_size):
                 # Convolution Layer
                 filter_shape = [filter_size, embedding_size, 1, num_filters]
-                W = tf.Variable(tf.truncated_normal(filter_shape, stddev=0.1), name="W")
-                b = tf.Variable(tf.constant(0.1, shape=[num_filters]), name="b")
+                W = tf.get_variable("W", tf.truncated_normal(filter_shape, stddev=0.1))
+                b = tf.Variable("b", tf.constant(0.1, shape=[num_filters]))
                 conv = tf.nn.conv2d(
                     self.embedded_chars_expanded,
                     W,
@@ -65,27 +63,27 @@ class TextCNN(object):
         self.h_pool_flat = tf.reshape(self.h_pool, [-1, num_filters_total])
 
         # Add dropout
-        with tf.name_scope("dropout"):
+        with tf.variable_scope("dropout"):
             self.h_drop = tf.nn.dropout(self.h_pool_flat, self.dropout_keep_prob)
 
         # Final (unnormalized) scores and predictions
-        with tf.name_scope("output"):
+        with tf.variable_scope("output"):
             W = tf.get_variable(
                 "W",
                 shape=[num_filters_total, num_classes],
                 initializer=tf.contrib.layers.xavier_initializer())
-            b = tf.Variable(tf.constant(0.1, shape=[num_classes]), name="b")
+            b = tf.get_variable("b", tf.constant(0.1, shape=[num_classes]))
[…]

### 2017-12-02 dl_style_transfer/workspace/shallowCNN_transfer.py
Made transfer reuse variables. Bug still exists in regular train.

@@ -30,7 +30,7 @@ class TextCNN(object):
         l2_loss = tf.constant(0.0)
 
         # Embedding layer
-        with tf.name_scope("embedding"):
+        with tf.variable_scope("embedding", reuse=True):
             self.W = tf.get_variable(
                 name="W", trainable=False)
             self.embedded_chars = tf.nn.embedding_lookup(self.W, self.input_x)
@@ -39,7 +39,7 @@ class TextCNN(object):
         # Create a convolution + maxpool layer for each filter size
         pooled_outputs = []
         for i, filter_size in enumerate(self.filter_sizes):
-            with tf.name_scope("conv-maxpool-%s" % filter_size):
+            with tf.variable_scope("conv-maxpool-%s" % filter_size, reuse=True):
                 # Convolution Layer
                 filter_shape = [filter_size, self.embedding_size, 1, self.num_filters]
                 W = tf.get_variable(name="W", trainable=False)
@@ -67,11 +67,11 @@ class TextCNN(object):
         self.h_pool_flat = tf.reshape(self.h_pool, [-1, num_filters_total])
 
         # Add dropout
-        with tf.name_scope("dropout"):
+        with tf.variable_scope("dropout"):
             self.h_drop = tf.nn.dropout(self.h_pool_flat, self.dropout_keep_prob)
 
         # Final (unnormalized) scores and predictions
-        with tf.name_scope("output"):
+        with tf.variable_scope("output", reuse=True):
             W = tf.get_variable(
                 "W", trainable=False)
             b = tf.get_variable(name="b", trainable=False)

### 2017-12-02 dl_style_transfer/layers.py
RYAN PLZ DO NOT DELETE

@@ -1,0 +1,402 @@
+from __future__ import print_function
+from __future__ import division
+from __future__ import absolute_import
+
+import tensorflow as tf
+import numpy as np
+import math
+
+
+def batch_norm(x, phase_train, decay=0.9, custom_inits=None, scope=None):
+    """Creates a batch normalization layer.
+    Used to stabilize distribution of outputs from a layer. Typically used right before a non-linearity. Works on
+    n-dimensional data.
+    Ref.: http://stackoverflow.com/questions/33949786/how-could-i-use-batch-normalization-in-tensorflow
+    Ref.: https://arxiv.org/pdf/1502.03167.pdf
+    Args:
+        x:            Tensor, shaped `[batch, features...]` allowing it do be used with Conv or FC layers of any shape.
+        phase_train:  Boolean tensor, true indicates training phase.
+        decay:        Float. The decay to use for the exponential moving average.
+        custom_inits: Dict from strings to functions that take a shape and return a tensor. These functions
+                      are used to initialize the corresponding variable. If a variable is not in the dict, then it is
+                      initialized with the default initializer for that variable. If `None` use default initializers.
+        scope:        String or VariableScope to use as the scope. If `None`, use default naming scheme.
+    Returns:
+        normed, vars: `normed` is a tensor of the batch-normalized features, and has same shape as `input`.
+                      `vars` is a dict of the variables.
+    """
+    x = tf.convert_to_tensor(x)
+    x_shape = x.shape.as_list()  # Don't deal with a TensorShape and instead use a list
+
+    # Check to ensure the minimum shape is met and there are no unknown dims in important places
+    if None in x_shape[1:] or len(x_shape) < 2:
+        raise ValueError("`x.shape` must be [batch, ..., features].")
+
+    with tf.variable_scope(scope, default_name='BN'):
+        # Define default initializers for beta and gamma. These are functions from shape to tensor.
+        inits = {
+            'Beta': lambda shape: tf.constant(0., shape=shape),
+            'Gamma': lambda shape: tf.constant(1., shape=shape),
+        }
+        if custom_inits is not None:
+            inits.update(custom_inits)  # Overwrite default inits with `custom_inits`
+
+        beta = tf.get_variable('Beta', initializer=inits['Beta']([x_shape[-1]]))  # Learned mean
[…]

### 2017-12-02 dl_style_transfer/layers.py
Image reconstructions

@@ -7,7 +7,7 @@ import numpy as np
 import math
 
 
-def batch_norm(x, phase_train, decay=0.9, custom_inits=None, scope=None):
+def batch_norm(x, phase_train, decay=0.9, custom_inits=None, scope='BN'):
     """Creates a batch normalization layer.
     Used to stabilize distribution of outputs from a layer. Typically used right before a non-linearity. Works on
     n-dimensional data.
@@ -25,12 +25,12 @@ def batch_norm(x, phase_train, decay=0.9, custom_inits=None, scope=None):
         normed, vars: `normed` is a tensor of the batch-normalized features, and has same shape as `input`.
                       `vars` is a dict of the variables.
     """
-    x = tf.convert_to_tensor(x)
-    x_shape = x.shape.as_list()  # Don't deal with a TensorShape and instead use a list
+    # x = tf.convert_to_tensor(x)
+    # x_shape = x.shape.as_list()  # Don't deal with a TensorShape and instead use a list
 
     # Check to ensure the minimum shape is met and there are no unknown dims in important places
-    if None in x_shape[1:] or len(x_shape) < 2:
-        raise ValueError("`x.shape` must be [batch, ..., features].")
+    #if None in x_shape[1:] or len(x_shape) < 2:
+    #    raise ValueError("`x.shape` must be [batch, ..., features].")
 
     with tf.variable_scope(scope, default_name='BN'):
         # Define default initializers for beta and gamma. These are functions from shape to tensor.
@@ -41,8 +41,8 @@ def batch_norm(x, phase_train, decay=0.9, custom_inits=None, scope=None):
         if custom_inits is not None:
             inits.update(custom_inits)  # Overwrite default inits with `custom_inits`
 
-        beta = tf.get_variable('Beta', initializer=inits['Beta']([x_shape[-1]]))  # Learned mean
-        gamma = tf.get_variable('Gamma', initializer=inits['Gamma']([x_shape[-1]]))  # Learned std. dev.
+        beta = tf.get_variable('Beta', initializer=tf.constant(custom_inits['Beta'], shape=x.shape[-1]))  # Learned mean
+        gamma = tf.get_variable('Gamma', initializer=tf.constant(custom_inits['Gamma'], shape=x.shape[-1]))  # Learned stdev.
 
         # Get mean and variance over batch and spatial dims
[…]

### 2017-12-03 dl_style_transfer/image-reconstruction.py
Revert "Merge branch 'master' of https://github.com/CornellDataScience/Yelp-FA17"
This reverts commit 562e31fb2bc5d7c4d75d3cfbc35a24c729173ba7, reversing
changes made to a5504c946846d62f7cc7ec9506880423adc66426.

@@ -1,183 +1,0 @@
-import os
-import sys
-import numpy as np
-import scipy.io
-import scipy.misc
-import tensorflow as tf
-import matplotlib.pyplot as plt
-%matplotlib inline
-
-IMAGE_WIDTH = 32
-IMAGE_HEIGHT = 32
-COLOR_CHANNELS = 3
-
-WEIGHTS = 'cifar10vgg_numpy.npz'
-weights = np.load(WEIGHTS)
-
-def load_weights(layer_name):
-    layer_type = layer_name.split('_')[0]
-    layer_num = int(layer_name.split('_')[1])
-    W = weights["b'" + str(layer_name) + "/kernel:0'"]
-    b = weights["b'" + str(layer_name) + "/bias:0'"]
-    if layer_type == 'conv2d':
-        beta = weights["b'batch_normalization_" + str(layer_num) + "/beta:0'"]
-        gamma = weights["b'batch_normalization_" + str(layer_num) + "/gamma:0'"]
-        mov_mean = weights["b'batch_normalization_" + str(layer_num) + "/moving_mean:0'"]
-        mov_var = weights["b'batch_normalization_" + str(layer_num) + "/moving_variance:0'"]
-        return W, b, beta, gamma, mov_mean, mov_var
-    elif layer_type == 'dense':
-        if layer_num == 1:
-            beta = weights["b'batch_normalization_14/beta:0'"]
-            gamma = weights["b'batch_normalization_14/gamma:0'"]
-            mov_mean = weights["b'batch_normalization_14/moving_mean:0'"]
-            mov_var = weights["b'batch_normalization_14/moving_variance:0'"]
-            return W, b, beta, gamma, mov_mean, mov_var
-        else:
-            return W, b
-        
-def conv(inputs, n_filters, name):
-    W, b, beta, gamma, mov_mean, mov_var = load_weights(name)
-    activations = tf.layers.conv2d(inputs, n_filters, [3,3], 
-                                   padding='SAME',
-                                   activation=tf.nn.relu,
-                                   kernel_initializer=tf.constant_initializer(W),
-                                   bias_initializer=tf.constant_initializer(b),
-                                   trainable=False,
-                                   name=name)
-    """normed = tf.layers.batch_normalization(activations,
[…]

### 2017-12-03 dl_style_transfer/layers.py

@@ -1,401 +1,0 @@
-from __future__ import print_function
-from __future__ import division
-from __future__ import absolute_import
-
-import tensorflow as tf
-import numpy as np
-import math
-
-
-def batch_norm(x, phase_train, decay=0.9, custom_inits=None, scope='BN'):
-    """Creates a batch normalization layer.
-    Used to stabilize distribution of outputs from a layer. Typically used right before a non-linearity. Works on
-    n-dimensional data.
-    Ref.: http://stackoverflow.com/questions/33949786/how-could-i-use-batch-normalization-in-tensorflow
-    Ref.: https://arxiv.org/pdf/1502.03167.pdf
-    Args:
-        x:            Tensor, shaped `[batch, features...]` allowing it do be used with Conv or FC layers of any shape.
-        phase_train:  Boolean tensor, true indicates training phase.
-        decay:        Float. The decay to use for the exponential moving average.
-        custom_inits: Dict from strings to functions that take a shape and return a tensor. These functions
-                      are used to initialize the corresponding variable. If a variable is not in the dict, then it is
-                      initialized with the default initializer for that variable. If `None` use default initializers.
-        scope:        String or VariableScope to use as the scope. If `None`, use default naming scheme.
-    Returns:
-        normed, vars: `normed` is a tensor of the batch-normalized features, and has same shape as `input`.
-                      `vars` is a dict of the variables.
-    """
-    # x = tf.convert_to_tensor(x)
-    # x_shape = x.shape.as_list()  # Don't deal with a TensorShape and instead use a list
-
-    # Check to ensure the minimum shape is met and there are no unknown dims in important places
-    #if None in x_shape[1:] or len(x_shape) < 2:
-    #    raise ValueError("`x.shape` must be [batch, ..., features].")
-
-    with tf.variable_scope(scope, default_name='BN'):
-        # Define default initializers for beta and gamma. These are functions from shape to tensor.
-        inits = {
-            'Beta': lambda shape: tf.constant(0., shape=shape),
-            'Gamma': lambda shape: tf.constant(1., shape=shape),
-        }
-        if custom_inits is not None:
-            inits.update(custom_inits)  # Overwrite default inits with `custom_inits`
-
-        beta = tf.get_variable('Beta', initializer=tf.constant(custom_inits['Beta'], shape=x.shape[-1]))  # Learned mean
[…]

### 2017-12-03 dl_style_transfer/workspace/shallowCNN.py
Fixed bug preventing shallowCNN from training. Worked towards making reconstruct work

@@ -38,8 +38,8 @@ class TextCNN(object):
             with tf.variable_scope("conv-maxpool-%s" % filter_size):
                 # Convolution Layer
                 filter_shape = [filter_size, embedding_size, 1, num_filters]
-                W = tf.get_variable("W", tf.truncated_normal(filter_shape, stddev=0.1))
-                b = tf.Variable("b", tf.constant(0.1, shape=[num_filters]))
+                W = tf.get_variable("W", initializer=tf.truncated_normal(filter_shape, stddev=0.1))
+                b = tf.get_variable("b", initializer=tf.constant(0.1, shape=[num_filters]))
                 conv = tf.nn.conv2d(
                     self.embedded_chars_expanded,
                     W,
@@ -72,7 +72,7 @@ class TextCNN(object):
                 "W",
                 shape=[num_filters_total, num_classes],
                 initializer=tf.contrib.layers.xavier_initializer())
-            b = tf.get_variable("b", tf.constant(0.1, shape=[num_classes]))
+            b = tf.get_variable("b", initializer=tf.constant(0.1, shape=[num_classes]))
             l2_loss += tf.nn.l2_loss(W)
             l2_loss += tf.nn.l2_loss(b)
             self.scores = tf.nn.xw_plus_b(self.h_drop, W, b, name="scores")

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py

@@ -5,7 +5,7 @@ import os
 import time
 import datetime
 import data_helpers
-from shallowCNN import TextCNN
+from shallowCNN_transfer import TextCNN
 from tensorflow.contrib import learn
 
 # Parameters
@@ -22,6 +22,8 @@ tf.flags.DEFINE_string("filter_sizes", "3,4,5", "Comma-separated filter sizes (d
 tf.flags.DEFINE_integer("num_filters", 128, "Number of filters per filter size (default: 128)")
 tf.flags.DEFINE_float("dropout_keep_prob", 0.5, "Dropout keep probability (default: 0.5)")
 tf.flags.DEFINE_float("l2_reg_lambda", 0.0, "L2 regularization lambda (default: 0.0)")
+tf.flags.DEFINE_integer("num_reconstructions", 1, "Number of reconstructions to built (default: 1)")
+
 
 # Training parameters
 tf.flags.DEFINE_integer("batch_size", 64, "Batch Size (default: 64)")
@@ -78,14 +80,10 @@ with tf.Graph().as_default():
     sess = tf.Session(config=session_conf)
     with sess.as_default():
         cnn = TextCNN(
+            num_reconstructions=FLAGS.num_reconstructions,
             sequence_length=x_train.shape[1],
-            num_classes=y_train.shape[1],
-            vocab_size=len(vocab_processor.vocabulary_),
-            embedding_size=FLAGS.embedding_dim,
             filter_sizes=list(map(int, FLAGS.filter_sizes.split(","))),
-            num_filters=FLAGS.num_filters,
-            l2_reg_lambda=FLAGS.l2_reg_lambda)
-
+            num_filters=FLAGS.num_filters)
         # Define Training procedure
         global_step = tf.Variable(0, name="global_step", trainable=False)
         optimizer = tf.train.AdamOptimizer(1e-3)

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_transfer.py

@@ -2,6 +2,7 @@ import tensorflow as tf
 import numpy as np
 import sys
 import os
+
 sys.path.append(os.path.abspath('../'))
 from dl_style_transfer.layers.layers import xavier_initializer
 
@@ -11,19 +12,17 @@ class TextCNN(object):
     A CNN for text classification.
     Uses an embedding layer, followed by a convolutional, max-pooling and softmax layer.
     """
+
     def __init__(
-      self, num_reconstructions, trained_model):
+            self, num_reconstructions, sequence_length, filter_sizes, num_filters):
         self.num_reconstructions = num_reconstructions
-        self.sequence_length = trained_model.sequence_length
-        self.num_classes = trained_model.num_classes
-        self.vocab_size = trained_model.vocab_size
-        self.embedding_size = trained_model.embedding_size
-        self.filter_sizes = trained_model.filter_sizes
-        self.num_filters = trained_model.num_filters
-        self.l2_reg_lambda = trained_model.l2_reg_lambda
+        self.sequence_length = sequence_length
+        self.filter_sizes = filter_sizes
+        self.num_filters = num_filters
 
         # Placeholders for input, output and dropout
-        self.input_x = tf.get_variable("input_x", shape=[self.num_reconstructions, self.sequence_length], trainable=False)
+        self.input_x = tf.get_variable("input_x", shape=[self.num_reconstructions, self.sequence_length],
+                                       trainable=False)
         self.dropout_keep_prob = tf.placeholder(tf.float32, name="dropout_keep_prob")
 
         # Keeping track of l2 regularization loss (optional)
@@ -41,7 +40,7 @@ class TextCNN(object):
         for i, filter_size in enumerate(self.filter_sizes):
             with tf.variable_scope("conv-maxpool-%s" % filter_size, reuse=True):
                 # Convolution Layer
-                filter_shape = [filter_size, self.embedding_size, 1, self.num_filters]
+                # filter_shape = [filter_size, self.embedding_size, 1, self.num_filters]
                 W = tf.get_variable(name="W", trainable=False)
                 b = tf.get_variable(name="b", trainable=False)
                 conv = tf.nn.conv2d(

### 2017-12-03 dl_style_transfer/workspace/shallowCNN.py
Made reconstruction restore variables properly (I think)

@@ -34,6 +34,7 @@ class TextCNN(object):
 
         # Create a convolution + maxpool layer for each filter size
         pooled_outputs = []
+        activations = []
         for i, filter_size in enumerate(filter_sizes):
             with tf.variable_scope("conv-maxpool-%s" % filter_size):
                 # Convolution Layer
@@ -44,23 +45,25 @@ class TextCNN(object):
                     self.embedded_chars_expanded,
                     W,
                     strides=[1, 1, 1, 1],
-                    padding="VALID",
+                    padding="SAME",
                     name="conv")
                 # Apply nonlinearity
                 h = tf.nn.relu(tf.nn.bias_add(conv, b), name="relu")
+                activations.append(h)
                 # Maxpooling over the outputs
                 pooled = tf.nn.max_pool(
                     h,
                     ksize=[1, sequence_length - filter_size + 1, 1, 1],
                     strides=[1, 1, 1, 1],
-                    padding='VALID',
+                    padding='SAME',
                     name="pool")
                 pooled_outputs.append(pooled)
 
         # Combine all the pooled features
         num_filters_total = num_filters * len(filter_sizes)
-        self.h_pool = tf.concat(pooled_outputs, 3)
+        self.h_pool = tf.concat(pooled_outputs, axis=3)
         self.h_pool_flat = tf.reshape(self.h_pool, [-1, num_filters_total])
+        self.activations_concat = tf.concat(activations, axis=3)
 
         # Add dropout
         with tf.variable_scope("dropout"):

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py

@@ -11,6 +11,10 @@ from tensorflow.contrib import learn
 # Parameters
 # ==================================================
 
+# Model Initialization
+tf.flags.DEFINE_string("model_path", "", "Path to the trained model.")
+
+
 # Data loading params
 tf.flags.DEFINE_float("dev_sample_percentage", .1, "Percentage of the training data to use for validation")
 tf.flags.DEFINE_string("positive_data_file", "./data/rt-polaritydata/rt-polarity.pos", "Data source for the positive data.")
@@ -78,12 +82,23 @@ with tf.Graph().as_default():
       allow_soft_placement=FLAGS.allow_soft_placement,
       log_device_placement=FLAGS.log_device_placement)
     sess = tf.Session(config=session_conf)
-    with sess.as_default():
+    with sess.as_default() as sess:
+        if FLAGS.model_path in (None, ""):
+            raise ValueError("`model_path` must be specified, but was:", FLAGS.model_path)
+
+        print("Loading saved model")
+        restore_saver = tf.train.import_meta_graph(FLAGS.model_path + ".meta")  # Construct the graph
+        restore_saver.restore(sess, FLAGS.model_path)  # Initialize the variables
+
+        print([n.name for n in tf.get_default_graph().as_graph_def().node if "Variable" in n.op])
+
         cnn = TextCNN(
             num_reconstructions=FLAGS.num_reconstructions,
             sequence_length=x_train.shape[1],
             filter_sizes=list(map(int, FLAGS.filter_sizes.split(","))),
             num_filters=FLAGS.num_filters)
+        sess.run(cnn.init_op)  # Initialize the cnn
+
         # Define Training procedure
         global_step = tf.Variable(0, name="global_step", trainable=False)
         optimizer = tf.train.AdamOptimizer(1e-3)

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_transfer.py

@@ -21,36 +21,38 @@ class TextCNN(object):
         self.num_filters = num_filters
 
         # Placeholders for input, output and dropout
-        self.input_x = tf.get_variable("input_x", shape=[self.num_reconstructions, self.sequence_length],
-                                       trainable=False)
         self.dropout_keep_prob = tf.placeholder(tf.float32, name="dropout_keep_prob")
 
-        # Keeping track of l2 regularization loss (optional)
-        l2_loss = tf.constant(0.0)
+        self.reconstructed = tf.get_variable(
+            "input_x",
+            initializer=xavier_initializer(shape=[self.num_reconstructions, self.sequence_length]))
 
         # Embedding layer
-        with tf.variable_scope("embedding", reuse=True):
+        with tf.variable_scope("embedding"):
             self.W = tf.get_variable(
                 name="W", trainable=False)
-            self.embedded_chars = tf.nn.embedding_lookup(self.W, self.input_x)
+            self.embedded_chars = tf.nn.embedding_lookup(self.W, self.reconstructed)
             self.embedded_chars_expanded = tf.expand_dims(self.embedded_chars, -1)
 
         # Create a convolution + maxpool layer for each filter size
         pooled_outputs = []
+        activations = []
         for i, filter_size in enumerate(self.filter_sizes):
-            with tf.variable_scope("conv-maxpool-%s" % filter_size, reuse=True):
+            with tf.variable_scope("conv-maxpool-%s" % filter_size):
                 # Convolution Layer
                 # filter_shape = [filter_size, self.embedding_size, 1, self.num_filters]
                 W = tf.get_variable(name="W", trainable=False)
+                print(W.initializer)
                 b = tf.get_variable(name="b", trainable=False)
                 conv = tf.nn.conv2d(
                     self.embedded_chars_expanded,
                     W,
                     strides=[1, 1, 1, 1],
-                    padding="VALID",
+                    padding="SAME",
                     name="conv")
                 # Apply nonlinearity
                 h = tf.nn.relu(tf.nn.bias_add(conv, b), name="relu")
+                activations.append(h)
                 # Maxpooling over the outputs
                 pooled = tf.nn.max_pool(
                     h,
@@ -62,19 +64,21 @@ class TextCNN(object):
 
         # Combine all the pooled features
         num_filters_total = self.num_filters * len(self.filter_sizes)
[…]

### 2017-12-03 dl_style_transfer/paper/main.tex
Updated paper

@@
 Although this modified network is far less generalizable in terms of classification, we found that the content representations provided by later layers of the network were still informative enough to reconstruct the original image, even for images containing objects not included in the 10 classes of CIFAR-10.
+By reconstruction, we refer to treating the input to the network as a variable, and minimizing $\ell_2$ loss between the input image and original image's feature representations in a certain layer.
+
+\begin{figure}[h]
+\subfloat{\includegraphics[width = .15\linewidth]{cornell-campus-small.jpg}}
+\hspace{0.1cm}
+\subfloat{\includegraphics[width = .15\linewidth]{anderson-small.jpg}}
+\hspace{0.1cm}
+\subfloat{\includegraphics[width = .15\linewidth]{boats.jpg}}
+\hspace{0.1cm}
+\subfloat{\includegraphics[width = .15\linewidth]{whale.jpg}}
+\hspace{0.1cm} 
+\subfloat{\includegraphics[width = .15\linewidth]{pizza.jpg}}
+\hspace{0.1cm} \\
+\subfloat{\includegraphics[width = .15\linewidth]{2600.png}}
+\hspace{0.1cm}
+\subfloat{\includegraphics[width = .15\linewidth]{anderson5800.png}}
+\hspace{0.1cm}
+\subfloat{\includegraphics[width = .15\linewidth]{boats2100.png}}
+\hspace{0.1cm}
+\subfloat{\includegraphics[width = .15\linewidth]{boats3200.png}}
+\hspace{0.1cm}
+\subfloat{\includegraphics[width = .15\linewidth]{pizza5000.png}}
+\hspace{0.1cm} \\
+\subfloat{\includegraphics[width = .15\linewidth]{corne9900.png}}
+\hspace{0.1cm}
+\subfloat{\includegraphics[width = .15\linewidth]{ander9900.png}}
+\hspace{0.1cm}
+\subfloat{\includegraphics[width = .15\linewidth]{boats9900.png}}
+\hspace	{0.1cm}
+\subfloat{\includegraphics[width = .15\linewidth]{whale9900.png}}
+\hspace{0.1cm}
+\subfloat{\includegraphics[width = .15\linewidth]{pizza9900.png}}
+\hspace{0.1cm}
+\caption{\textmd{Several 32x32 images (top) reconstructed in the conv2\_2 layer (middle) and conv4\_2 layer (bottom) of VGG-19 trained on CIFAR-10 data; maximum 10000 iterations.}}
+\end{figure}
+
+In the reconstruction phase, we use average-pooling in place of max-pooling, as suggested in \cite{GatysEB15a}.
+Although none of the images in Figure 2 resemble any of the ten classes present in CIFAR-10 data, the network still produces highly informative feature representations through convolution.
+This is a key observation in making the transition to text data, as writing style is subjective and therefore it is difficult to collect data from a large number of distinct classes that span the entire space of writing styles.
+
+However, we also observe that this reduction in generalizability of the underlying network architecture is not without tradeoffs.
+When using the conv4\_2 layer at which to match the feature representations of two images (the layer used in Figure 1), the reconstructed images are mostly unrecognizable to the human eye, and takes a much larger number of iterations to produce something even remotely close to the original.
+While we do not dismiss the possibility that this loss in reconstruction accuracy could be mitigated by hyperparameter optimization, we conclude that high generalizability as a classifier is an important quality of the underlying architecture although not paramount.
 
@@
 Here, we propose a generalization of $k$-competitive layers to convolutional layers.
+Let $z_{ijk}$ be the activation volume produced by a convolutional layer, where $z_{x,y,:}$ denotes the feature vector at spatial location $(x,y)$.
+Then, we define the \textbf{energy map} of an activation volume, $E$, as the matrix with entries:
+$$e_{ij} = \sum_{k=1}^K |z_{ijk}|$$
+We then perform a $k$-competitive non-linearity, where we select the $k$ most competitive entries, and masking the activations of the ``loser'' neurons while augmenting the activations of the ``winner'' neurons.
+If we denote the set of indices of the $k$ ``winner'' neurons by $C_k$, then:
+$$kcomp(z)_{i,j,:} = \textbf{0} \hspace{0.5cm} \forall (i,j) \notin C_k$$
+$$kcomp(z)_{i,j,:} = z_{i,j,:} + \alpha\sum_{(i,j) \notin C_k} z_{i,j,:} \hspace{0.5cm} \forall (i,j) \in C_k$$
+where $\alpha$, the amplification constant, is a hyperparameter.
 
@@
 
+\subsection{Comparison of Architectures}
+
 \subsection{Hyperparameters and Training}
-
-\subsection{Comparison of Architectures}
 

### 2017-12-03 dl_style_transfer/workspace/shallowCNN.py
Undid

@@ -34,7 +34,7 @@ class TextCNN(object):
 
         # Create a convolution + maxpool layer for each filter size
         pooled_outputs = []
-        activations = []
+        #activations = []
         for i, filter_size in enumerate(filter_sizes):
             with tf.variable_scope("conv-maxpool-%s" % filter_size):
                 # Convolution Layer
@@ -45,25 +45,29 @@ class TextCNN(object):
                     self.embedded_chars_expanded,
                     W,
                     strides=[1, 1, 1, 1],
-                    padding="SAME",
+                    padding="VALID",
                     name="conv")
                 # Apply nonlinearity
+                print("conv shape:", conv.shape, filter_size)
                 h = tf.nn.relu(tf.nn.bias_add(conv, b), name="relu")
-                activations.append(h)
+                #activations.append(h)
                 # Maxpooling over the outputs
                 pooled = tf.nn.max_pool(
                     h,
                     ksize=[1, sequence_length - filter_size + 1, 1, 1],
                     strides=[1, 1, 1, 1],
-                    padding='SAME',
+                    padding='VALID',
                     name="pool")
+                print("pooled shape:", pooled.shape, filter_size)
                 pooled_outputs.append(pooled)
 
         # Combine all the pooled features
         num_filters_total = num_filters * len(filter_sizes)
         self.h_pool = tf.concat(pooled_outputs, axis=3)
+        print(self.h_pool.shape)
         self.h_pool_flat = tf.reshape(self.h_pool, [-1, num_filters_total])
-        self.activations_concat = tf.concat(activations, axis=3)
+        print(self.h_pool_flat.shape)
+        #self.activations_concat = tf.concat(activations, axis=3)
 
         # Add dropout
         with tf.variable_scope("dropout"):
@@ -79,7 +83,7 @@ class TextCNN(object):
             l2_loss += tf.nn.l2_loss(W)
             l2_loss += tf.nn.l2_loss(b)
             self.scores = tf.nn.xw_plus_b(self.h_drop, W, b, name="scores")
-            self.predictions = tf.argmax(self.scores, 1, name="predictions")
+            self.predictions = tf.argmax(self.scores, -1, name="predictions")
 
         # Calculate mean cross-entropy loss
         with tf.variable_scope("loss"):
@@ -88,5 +92,5 @@ class TextCNN(object):
 
         # Accuracy
         with tf.variable_scope("accuracy"):
[…]

### 2017-12-03 dl_style_transfer/workspace/shallowCNN.py
Fixed bug due to VALID vs SAME pooling/convolutions

@@ -34,7 +34,6 @@ class TextCNN(object):
 
         # Create a convolution + maxpool layer for each filter size
         pooled_outputs = []
-        #activations = []
         for i, filter_size in enumerate(filter_sizes):
             with tf.variable_scope("conv-maxpool-%s" % filter_size):
                 # Convolution Layer
@@ -50,7 +49,7 @@ class TextCNN(object):
                 # Apply nonlinearity
                 print("conv shape:", conv.shape, filter_size)
                 h = tf.nn.relu(tf.nn.bias_add(conv, b), name="relu")
-                #activations.append(h)
+
                 # Maxpooling over the outputs
                 pooled = tf.nn.max_pool(
                     h,
@@ -67,7 +66,6 @@ class TextCNN(object):
         print(self.h_pool.shape)
         self.h_pool_flat = tf.reshape(self.h_pool, [-1, num_filters_total])
         print(self.h_pool_flat.shape)
-        #self.activations_concat = tf.concat(activations, axis=3)
 
         # Add dropout
         with tf.variable_scope("dropout"):

### 2017-12-03 dl_style_transfer/workspace/shallowCNN.py
Removed debugging print statements in shallowCNN.py

@@ -47,9 +47,7 @@ class TextCNN(object):
                     padding="VALID",
                     name="conv")
                 # Apply nonlinearity
-                print("conv shape:", conv.shape, filter_size)
                 h = tf.nn.relu(tf.nn.bias_add(conv, b), name="relu")
-
                 # Maxpooling over the outputs
                 pooled = tf.nn.max_pool(
                     h,
@@ -57,15 +55,12 @@ class TextCNN(object):
                     strides=[1, 1, 1, 1],
                     padding='VALID',
                     name="pool")
-                print("pooled shape:", pooled.shape, filter_size)
                 pooled_outputs.append(pooled)
 
         # Combine all the pooled features
         num_filters_total = num_filters * len(filter_sizes)
         self.h_pool = tf.concat(pooled_outputs, axis=3)
-        print(self.h_pool.shape)
         self.h_pool_flat = tf.reshape(self.h_pool, [-1, num_filters_total])
-        print(self.h_pool_flat.shape)
 
         # Add dropout
         with tf.variable_scope("dropout"):

### 2017-12-03 dl_style_transfer/workspace/shallowCNN.py
trained kate onehot, added code for loading and training cnn kate hybrid

@@ -1,6 +1,8 @@
 import tensorflow as tf
 import numpy as np
 
+from layers import layers
+
 
 class TextCNN(object):
     """

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
Fixed last shape bug for reconstruction, made reconstruction variable

@@ -89,14 +89,16 @@ with tf.Graph().as_default():
         print("Loading saved model")
         restore_saver = tf.train.import_meta_graph(FLAGS.model_path + ".meta")  # Construct the graph
         restore_saver.restore(sess, FLAGS.model_path)  # Initialize the variables
-
-        print([n.name for n in tf.get_default_graph().as_graph_def().node if "Variable" in n.op])
-
+        print("Constructing Reconstruction Graph...")
         cnn = TextCNN(
             num_reconstructions=FLAGS.num_reconstructions,
             sequence_length=x_train.shape[1],
+            num_classes=y_train.shape[1],
+            vocab_size=len(vocab_processor.vocabulary_),
+            embedding_size=FLAGS.embedding_dim,
             filter_sizes=list(map(int, FLAGS.filter_sizes.split(","))),
-            num_filters=FLAGS.num_filters)
+            num_filters=FLAGS.num_filters,
+            l2_reg_lambda=FLAGS.l2_reg_lambda)
         sess.run(cnn.init_op)  # Initialize the cnn
 
         # Define Training procedure

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_transfer.py

@@ -14,35 +14,37 @@ class TextCNN(object):
     """
 
     def __init__(
-            self, num_reconstructions, sequence_length, filter_sizes, num_filters):
+            self, num_reconstructions, sequence_length, num_classes, vocab_size,
+            embedding_size, filter_sizes, num_filters, l2_reg_lambda=0.0):
         self.num_reconstructions = num_reconstructions
         self.sequence_length = sequence_length
+        self.num_classes = num_classes
+        self.vocab_size = vocab_size
+        self.embedding_size = embedding_size
         self.filter_sizes = filter_sizes
         self.num_filters = num_filters
+        self.l2_reg_lambda = l2_reg_lambda
 
         # Placeholders for input, output and dropout
         self.dropout_keep_prob = tf.placeholder(tf.float32, name="dropout_keep_prob")
 
-        self.reconstructed = tf.get_variable(
-            "input_x",
-            initializer=xavier_initializer(shape=[self.num_reconstructions, self.sequence_length]))
-
         # Embedding layer
         with tf.variable_scope("embedding"):
-            self.W = tf.get_variable(
-                name="W", trainable=False)
-            self.embedded_chars = tf.nn.embedding_lookup(self.W, self.reconstructed)
-            self.embedded_chars_expanded = tf.expand_dims(self.embedded_chars, -1)
+
+            self.reconstructions = tf.get_variable(
+                name="Reconstructions",
+                initializer=xavier_initializer([num_reconstructions, sequence_length, embedding_size]))
+            self.embedded_chars_expanded = tf.expand_dims(self.reconstructions, -1)
 
         # Create a convolution + maxpool layer for each filter size
         pooled_outputs = []
-        activations = []
+        self.activations = []
         for i, filter_size in enumerate(self.filter_sizes):
             with tf.variable_scope("conv-maxpool-%s" % filter_size):
                 # Convolution Layer
-                W = tf.get_variable(name="W", trainable=False)
-                print(W.initializer)
-                b = tf.get_variable(name="b", trainable=False)
+                filter_shape = [filter_size, embedding_size, 1, num_filters]
+                W = tf.get_variable(name="W", shape=filter_shape, trainable=False)
+                b = tf.get_variable(name="b", shape=[num_filters], trainable=False)
                 conv = tf.nn.conv2d(
                     self.embedded_chars_expanded,
                     W,
@@ -51,7 +53,7 @@ class TextCNN(object):
                     name="conv")
[…]

### 2017-12-03 dl_style_transfer/workspace/kate_new.py
updated loss of kate so that it is conditional on input type

@@ -13,14 +13,14 @@ from time import time, strftime
 
 class Kate:
 
-    def __init__(self, embedding_size_in, embedding_size_out, expand_hot, k, alpha, learning_rate=0.001, load_model=None):
+    def __init__(self, embedding_size_in, embedding_size_out, is_hot, k, alpha, learning_rate=0.001, load_model=None):
         """Initializes the KATE model. Does not perform any training.
 ,
         Args:
             embedding_size_in:  The size of the input embeddings. If `expand_hot` is `True`, this is the size of the one
                                 hot vectors that will be generated.
             embedding_size_out: The size of the output embeddings. This is the size of the encoded vectors.
-            expand_hot:         Boolean determining if the input represents indices of a word list to be expanded using
+            is_hot:             Boolean determining if the input represents bag of words or one hot representation
                                 a one-hot representation.
             k:                  The number of neurons to keep in the k-competitive layer.
             alpha:              Sets the intensity of the energy redistribution in the k-comptitive layer.
@@ -30,7 +30,7 @@ class Kate:
         """
         self._embedding_size_in = embedding_size_in
         self._embedding_size_out = embedding_size_out
-        self._expand_hot = expand_hot
+        self._is_hot = is_hot
         self._k = k
         self._alpha = alpha
 
@@ -39,7 +39,7 @@ class Kate:
         with self._graph.as_default():
             self._phase_train = tf.placeholder(tf.bool, name='Phase')
 
-            if expand_hot:
+            if is_hot:
                 self._x = tf.placeholder(tf.int32, shape=[None], name='X')
                 self._embedding = tf.one_hot(self._x, depth=embedding_size_in, name='Embedding')
             else:
@@ -59,7 +59,10 @@ class Kate:
                 self._argmax = tf.argmax(self._decoded, axis=-1, name='Decoded-Argmax')
 
             with tf.variable_scope('Loss'):
-                self._loss = tf.reduce_mean(tf.nn.softmax_cross_entropy_with_logits(logits=scores, labels=self._embedding, name='Loss'))
+                if is_hot:
+                    self._loss = tf.reduce_mean(tf.nn.softmax_cross_entropy_with_logits(logits=scores, labels=self._embedding, name='Loss'))
+                else:
+                    self._loss = tf.reduce_mean(tf.nn.sigmoid_cross_entropy_with_logits(logits=scores, labels=self._embedding, name='Loss'))
[…]

### 2017-12-03 dl_style_transfer/workspace/kate_new.py
Fixed minor bug when choosing between softmax and sigmoid

@@ -20,8 +20,8 @@ class Kate:
             embedding_size_in:  The size of the input embeddings. If `expand_hot` is `True`, this is the size of the one
                                 hot vectors that will be generated.
             embedding_size_out: The size of the output embeddings. This is the size of the encoded vectors.
-            is_hot:             Boolean determining if the input represents bag of words or one hot representation
-                                a one-hot representation.
+            is_hot:             Boolean determining if the input is a log normalized bag of words, or if it is a list of
+                                indices to be expanded to a one-hot representation.
             k:                  The number of neurons to keep in the k-competitive layer.
             alpha:              Sets the intensity of the energy redistribution in the k-comptitive layer.
             learning_rate:      The learning rate for training.
@@ -55,14 +55,12 @@ class Kate:
                 bias = tf.get_variable('Scores', initializer=xavier_initializer((embedding_size_in,)))
                 scores = tf.matmul(self._encoded, weights) + bias  # `[batch*max_seq_len, embedding_size_in]
 
-                self._decoded = tf.nn.softmax(scores, name='Decoded')
+                self._decoded = (tf.nn.softmax if is_hot else tf.nn.sigmoid)(scores, name='Decoded')
                 self._argmax = tf.argmax(self._decoded, axis=-1, name='Decoded-Argmax')
 
             with tf.variable_scope('Loss'):
-                if is_hot:
-                    self._loss = tf.reduce_mean(tf.nn.softmax_cross_entropy_with_logits(logits=scores, labels=self._embedding, name='Loss'))
-                else:
-                    self._loss = tf.reduce_mean(tf.nn.sigmoid_cross_entropy_with_logits(logits=scores, labels=self._embedding, name='Loss'))
+                loss_fn = tf.nn.softmax_cross_entropy_with_logits if is_hot else tf.nn.sigmoid_cross_entropy_with_logits
+                self._loss = tf.reduce_mean(loss_fn(logits=scores, labels=self._embedding, name='Loss'))
                 self._train_step = tf.train.AdamOptimizer(learning_rate).minimize(self._loss)
 
             self._sess = tf.Session()

### 2017-12-03 dl_style_transfer/workspace/shallowCNN.py
Making reconstruction loss is in-progress

@@ -1,8 +1,6 @@
 import tensorflow as tf
 import numpy as np
 
-from layers import layers
-
 
 class TextCNN(object):
     """

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py

@@ -99,7 +99,14 @@ with tf.Graph().as_default():
             filter_sizes=list(map(int, FLAGS.filter_sizes.split(","))),
             num_filters=FLAGS.num_filters,
             l2_reg_lambda=FLAGS.l2_reg_lambda)
+
         sess.run(cnn.init_op)  # Initialize the cnn
+
+        # Expand data into the embeddings
+        data_batch = x_train[:1]
+        embeddings_batch = np.zeros(data_batch.shape + [FLAGS.embedding_dim])
+        # Assign reconstruction matrix to data_batch
+        target_content = sess.run(cnn.activation)
 
         # Define Training procedure
         global_step = tf.Variable(0, name="global_step", trainable=False)

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_train_simplified.py

@@ -86,6 +86,8 @@ with tf.Graph().as_default():
             num_filters=FLAGS.num_filters,
             l2_reg_lambda=FLAGS.l2_reg_lambda)
 
+        print(x_train.shape)
+        print(x_train[1, ...])
         # Define Training procedure
         global_step = tf.Variable(0, name="global_step", trainable=False)
         optimizer = tf.train.AdamOptimizer(1e-3)

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
Added an s

@@ -106,7 +106,7 @@ with tf.Graph().as_default():
         data_batch = x_train[:1]
         embeddings_batch = np.zeros(data_batch.shape + [FLAGS.embedding_dim])
         # Assign reconstruction matrix to data_batch
-        target_content = sess.run(cnn.activation)
+        target_content = sess.run(cnn.activations)
 
         # Define Training procedure
         global_step = tf.Variable(0, name="global_step", trainable=False)

### 2017-12-03 dl_style_transfer/train_kate_bag.py
Made save path for kate a command line argument

@@ -33,7 +33,7 @@ def train_batch(data, batch_size, epoch=100, start_stop_info=True, progress_inte
 
 
 train_batch(data, 128, 100)
-kate.save_model("saved/100-epoch/kate-bag-words-100.ckpt")
+kate.save_model(sys.argv[1])
 
 
 def random_sample(data, num_samples):

### 2017-12-03 dl_style_transfer/train_kate_embeds.py

@@ -16,7 +16,7 @@ dataset = yelp.get_ryans_strange_input()
 train, test = train_test_split(dataset)
 kate = Kate(yelp.vocab_length(), 128, True, 32, 6.26)
 kate.train(train, 100, 128)
-kate.save_model("saved/100-epoch/kate-hot-100.ckpt")
+kate.save_model(sys.argv[1])
 
 
 def random_sample(data, num_samples):

### 2017-12-03 dl_style_transfer/train_kate_bag.py
Added error message if kate is trained without a path

@@ -13,6 +13,11 @@ from time import time
 seed = 1337
 np.random.seed(seed)
 
+if len(sys.argv) is not 2:
+    raise ValueError("Please provide the path where KATE will be saved!")
+
+save_path = sys.argv[1]
+
 data = yelp.get_small_bag()
 train, test = train_test_split(data)
 kate = Kate(yelp.vocab_length(), 128, False, 32, 6.26)
@@ -33,7 +38,7 @@ def train_batch(data, batch_size, epoch=100, start_stop_info=True, progress_inte
 
 
 train_batch(data, 128, 100)
-kate.save_model(sys.argv[1])
+kate.save_model(save_path)
 
 
 def random_sample(data, num_samples):

### 2017-12-03 dl_style_transfer/train_kate_embeds.py

@@ -12,11 +12,16 @@ from time import time
 seed = 1337
 np.random.seed(seed)
 
+if len(sys.argv) is not 2:
+    raise ValueError("Please provide the path where KATE will be saved!")
+
+save_path = sys.argv[1]
+
 dataset = yelp.get_ryans_strange_input()
 train, test = train_test_split(dataset)
 kate = Kate(yelp.vocab_length(), 128, True, 32, 6.26)
 kate.train(train, 100, 128)
-kate.save_model(sys.argv[1])
+kate.save_model(save_path)
 
 
 def random_sample(data, num_samples):

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
One-hot encoding of sentences

@@ -7,6 +7,7 @@ import datetime
 import data_helpers
 from shallowCNN_transfer import TextCNN
 from tensorflow.contrib import learn
+from sklearn.preprocessing import OneHotEncoder
 
 # Parameters
 # ==================================================
@@ -105,6 +106,8 @@ with tf.Graph().as_default():
         # Expand data into the embeddings
         data_batch = x_train[:1]
         embeddings_batch = np.zeros(data_batch.shape + [FLAGS.embedding_dim])
+        for i, sentence in enumerate(x_train):
+            x_train[i] = np.array(OneHotEncoder().fit_transform(sentence).todense())
         # Assign reconstruction matrix to data_batch
         target_content = sess.run(cnn.activations)
 

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
Fixed typo

@@ -107,7 +107,7 @@ with tf.Graph().as_default():
         data_batch = x_train[:1]
         embeddings_batch = np.zeros(data_batch.shape + [FLAGS.embedding_dim])
         for i, sentence in enumerate(x_train):
-            x_train[i] = np.array(OneHotEncoder().fit_transform(sentence).todense())
+            embeddings_batch[i] = np.array(OneHotEncoder().fit_transform(sentence).todense())
         # Assign reconstruction matrix to data_batch
         target_content = sess.run(cnn.activations)
 

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
One-hot encoding

@@ -107,7 +107,7 @@ with tf.Graph().as_default():
         data_batch = x_train[:1]
         embeddings_batch = np.zeros(data_batch.shape + [FLAGS.embedding_dim])
         for i, sentence in enumerate(x_train):
-            embeddings_batch[i] = np.array(OneHotEncoder().fit_transform(sentence).todense())
+            embeddings_batch[i] = np.array(OneHotEncoder(n_values=len(vocab_processor.vocabulary_)).fit_transform(sentence).todense())
         # Assign reconstruction matrix to data_batch
         target_content = sess.run(cnn.activations)
 

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
Added content loss function

@@ -108,13 +108,17 @@ with tf.Graph().as_default():
         embeddings_batch = np.zeros(data_batch.shape + [FLAGS.embedding_dim])
         for i, sentence in enumerate(x_train):
             embeddings_batch[i] = np.array(OneHotEncoder(n_values=len(vocab_processor.vocabulary_)).fit_transform(sentence).todense())
-        # Assign reconstruction matrix to data_batch
-        target_content = sess.run(cnn.activations)
+
+        # Assign reconstruction tensor to data_batch to generatae target_content
+        target_content = sess.run(cnn.activations, feed_dict={cnn.reconstructions: embeddings_batch})
+        target_content = [tf.constant(target) for target in target_content]
+        losses = [tf.nn.l2_loss(target - activation) for target, activation in zip(target_content, cnn.activations)]
+        loss = tf.reduce_sum(losses)
 
         # Define Training procedure
         global_step = tf.Variable(0, name="global_step", trainable=False)
         optimizer = tf.train.AdamOptimizer(1e-3)
-        grads_and_vars = optimizer.compute_gradients(cnn.loss)
+        grads_and_vars = optimizer.compute_gradients(loss)
         train_op = optimizer.apply_gradients(grads_and_vars, global_step=global_step)
 
         # Output directory for models and summaries
@@ -128,9 +132,6 @@ with tf.Graph().as_default():
         if not os.path.exists(checkpoint_dir):
             os.makedirs(checkpoint_dir)
         saver = tf.train.Saver(tf.global_variables(), max_to_keep=FLAGS.num_checkpoints)
-
-        # Initialize all variables
-        sess.run(tf.global_variables_initializer())
 
         def train_step(x_batch, y_batch):
             """

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
One-hot encoding

@@ -107,7 +107,7 @@ with tf.Graph().as_default():
         data_batch = x_train[:1]
         embeddings_batch = np.zeros(data_batch.shape + [FLAGS.embedding_dim])
         for i, sentence in enumerate(x_train):
-            embeddings_batch[i] = np.array(OneHotEncoder(n_values=len(vocab_processor.vocabulary_)).fit_transform(sentence).todense())
+            embeddings_batch[i] = np.array(OneHotEncoder(n_values=len(vocab_processorx.vocabulary_)).fit_transform(sentence).todense())
         # Assign reconstruction matrix to data_batch
         target_content = sess.run(cnn.activations)
 

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
Added reconstruction training code

@@ -105,7 +105,7 @@ with tf.Graph().as_default():
 
         # Expand data into the embeddings
         data_batch = x_train[:1]
-        embeddings_batch = np.zeros(data_batch.shape + [FLAGS.embedding_dim])
+        embeddings_batch = np.zeros(data_batch.shape + (FLAGS.embedding_dim,))
         for i, sentence in enumerate(x_train):
             embeddings_batch[i] = np.array(OneHotEncoder(n_values=len(vocab_processor.vocabulary_)).fit_transform(sentence).todense())
 
@@ -121,60 +121,10 @@ with tf.Graph().as_default():
         grads_and_vars = optimizer.compute_gradients(loss)
         train_op = optimizer.apply_gradients(grads_and_vars, global_step=global_step)
 
-        # Output directory for models and summaries
-        timestamp = str(int(time.time()))
-        out_dir = os.path.abspath(os.path.join(os.path.curdir, "runs", timestamp))
-        print("Writing to {}\n".format(out_dir))
+        sess.run(tf.global_variables_initializer())
 
-        # Checkpoint directory. Tensorflow assumes this directory already exists so we need to create it
-        checkpoint_dir = os.path.abspath(os.path.join(out_dir, "checkpoints"))
-        checkpoint_prefix = os.path.join(checkpoint_dir, "model")
-        if not os.path.exists(checkpoint_dir):
-            os.makedirs(checkpoint_dir)
-        saver = tf.train.Saver(tf.global_variables(), max_to_keep=FLAGS.num_checkpoints)
-
-        def train_step(x_batch, y_batch):
-            """
-            A single training step
-            """
-            feed_dict = {
-              cnn.input_x: x_batch,
-              cnn.input_y: y_batch,
-              cnn.dropout_keep_prob: FLAGS.dropout_keep_prob
-            }
-            _, step, loss, accuracy = sess.run(
-                [train_op, global_step, cnn.loss, cnn.accuracy],
-                feed_dict)
-            time_str = datetime.datetime.now().isoformat()
-            print("{}: step {}, loss {:g}, acc {:g}".format(time_str, step, loss, accuracy))
-
-        def dev_step(x_batch, y_batch, writer=None):
-            """
-            Evaluates model on a dev set
-            """
-            feed_dict = {
-              cnn.input_x: x_batch,
-              cnn.input_y: y_batch,
-              cnn.dropout_keep_prob: 1.0
-            }
-            step, loss, accuracy = sess.run(
[…]

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
Some shitty code

@@ -107,8 +107,8 @@ with tf.Graph().as_default():
         data_batch = x_train[:1]
         embeddings_batch = np.zeros(data_batch.shape + [FLAGS.embedding_dim])
         for i, sentence in enumerate(x_train):
-            embeddings_batch[i] = np.array(OneHotEncoder(n_values=len(vocab_processor.vocabulary_)).fit_transform(sentence).todense())
-        
+            embeddings_batch[i] = np.array(OneHotEncoder(n_values=len(vocab_processor.vocabulary_).fit_transform(np.array(sentence).reshape(1, -1))).todense()).reshape(len(vocab_processor.vocabulary_), -1)
+
         # Assign reconstruction tensor to data_batch to generatae target_content
         target_content = sess.run(cnn.activations, feed_dict={cnn.reconstructions: embeddings_batch})
         target_content = [tf.constant(target) for target in target_content]

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
One-hot encoding

@@ -106,8 +106,9 @@ with tf.Graph().as_default():
         # Expand data into the embeddings
         data_batch = x_train[:1]
         embeddings_batch = np.zeros(data_batch.shape + (FLAGS.embedding_dim,))
+        n = len(vocab_processor.vocabulary_)
         for i, sentence in enumerate(x_train):
-            embeddings_batch[i] = np.array(OneHotEncoder(n_values=len(vocab_processor.vocabulary_).fit_transform(np.array(sentence).reshape(1, -1))).todense()).reshape(len(vocab_processor.vocabulary_), -1)
+            embeddings_batch[i] = np.array(OneHotEncoder(n_values=n).fit_transform(np.array(sentence).reshape(1, -1))).todense().reshape(n, -1)
 
         # Assign reconstruction tensor to data_batch to generatae target_content
         target_content = sess.run(cnn.activations, feed_dict={cnn.reconstructions: embeddings_batch})

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
Fixed one-hot encoding

@@ -108,7 +108,7 @@ with tf.Graph().as_default():
         embeddings_batch = np.zeros(data_batch.shape + (FLAGS.embedding_dim,))
         n = len(vocab_processor.vocabulary_)
         for i, sentence in enumerate(x_train):
-            embeddings_batch[i] = np.array(OneHotEncoder(n_values=n).fit_transform(np.array(sentence).reshape(1, -1))).todense().reshape(n, -1)
+            embeddings_batch[i] = np.array(OneHotEncoder(n_values=n).fit_transform(np.array(sentence).reshape(1, -1)).todense()).reshape(n, -1)
 
         # Assign reconstruction tensor to data_batch to generatae target_content
         target_content = sess.run(cnn.activations, feed_dict={cnn.reconstructions: embeddings_batch})

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
cyka blyat

@@ -9,6 +9,9 @@ from shallowCNN_transfer import TextCNN
 from tensorflow.contrib import learn
 from sklearn.preprocessing import OneHotEncoder
 
+import sys, os
+sys.path.append(os.path.abspath('../../'))
+
 # Parameters
 # ==================================================
 
@@ -108,7 +111,7 @@ with tf.Graph().as_default():
         embeddings_batch = np.zeros(data_batch.shape + (FLAGS.embedding_dim,))
         n = len(vocab_processor.vocabulary_)
         for i, sentence in enumerate(x_train):
-            embeddings_batch[i] = np.array(OneHotEncoder(n_values=n).fit_transform(np.array(sentence).reshape(1, -1)).todense()).reshape(n, -1)
+            embeddings_batch[i] = np.array(OneHotEncoder(n_values=n).fit_transform(np.array(sentence).reshape(1, -1)).todense()).reshape(-1, n)
 
         # Assign reconstruction tensor to data_batch to generatae target_content
         target_content = sess.run(cnn.activations, feed_dict={cnn.reconstructions: embeddings_batch})
@@ -129,3 +132,8 @@ with tf.Graph().as_default():
             _, loss = sess.run([train_op, loss])
             if i%50 == 0:
                 print("Loss:", loss)
+
+        reconstructions = sess.run(cnn.reconstructions)
+
+        # TODO: display reconstructions
+        argmax = np.argmax(reconstructions)

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
jfjfjf

@@ -11,6 +11,7 @@ from sklearn.preprocessing import OneHotEncoder
 
 import sys, os
 sys.path.append(os.path.abspath('../../'))
+import dl_style_transfer.layers.layers
 
 # Parameters
 # ==================================================

### 2017-12-03 dl_style_transfer/workspace/kate_new.py
Fixed progress reporting in kate.

@@ -107,8 +107,9 @@ class Kate:
             print("Starting training for %d epochs" % n_epochs)
 
         batch_per_epoch = math.ceil(training_size/batch_size)
-        n_batch = n_epochs*batch_per_epoch
+        n_iters = n_epochs*batch_per_epoch
         last_time = time()
+        count = 0
         for epoch in range(n_epochs):
             perm = np.random.permutation(training_size)
             for i in range(0, training_size, batch_size):
@@ -119,7 +120,8 @@ class Kate:
                 if progress_interval is not None and (current_time - last_time) >= progress_interval:
                     last_time = current_time
                     print("Current Loss Value: %.10f, Percent Complete: %.4f" %
-                          (loss_val, (epoch*batch_per_epoch + i) / n_batch * 100))
+                          (loss_val, count / n_iters * 100))
+            count += 1
         if start_stop_info:
             print("Completed Training.")
         return loss_val

### 2017-12-03 dl_style_transfer/workspace/kate_new.py
Made kate use sparse softmax when `is_hot` is true

@@ -59,8 +59,8 @@ class Kate:
                 self._argmax = tf.argmax(self._decoded, axis=-1, name='Decoded-Argmax')
 
             with tf.variable_scope('Loss'):
-                loss_fn = tf.nn.softmax_cross_entropy_with_logits if is_hot else tf.nn.sigmoid_cross_entropy_with_logits
-                self._loss = tf.reduce_mean(loss_fn(logits=scores, labels=self._embedding, name='Loss'))
+                loss_fn = tf.nn.sparse_softmax_cross_entropy_with_logits if is_hot else tf.nn.sigmoid_cross_entropy_with_logits
+                self._loss = tf.reduce_mean(loss_fn(logits=scores, labels=(self._x if is_hot else self._embedding), name='Loss'))
                 self._train_step = tf.train.AdamOptimizer(learning_rate).minimize(self._loss)
 
             self._sess = tf.Session()
@@ -119,9 +119,9 @@ class Kate:
                 current_time = time()
                 if progress_interval is not None and (current_time - last_time) >= progress_interval:
                     last_time = current_time
-                    print("Current Loss Value: %.10f, Percent Complete: %.4f" %
+                    print("Current Loss Value: %.10f, Percent Complete: %.6f" %
                           (loss_val, count / n_iters * 100))
-            count += 1
+                count += 1
         if start_stop_info:
             print("Completed Training.")
         return loss_val

### 2017-12-03 dl_style_transfer/train_kate_bag.py
Made models save on exit

@@ -1,6 +1,7 @@
 import numpy as np
 import os
 import sys
+import atexit
 
 sys.path.append(os.path.abspath('../'))
 
@@ -23,6 +24,11 @@ train, test = train_test_split(data)
 kate = Kate(yelp.vocab_length(), 128, False, 32, 6.26)
 # kate.train(train, 100, 128)
 
+def at_exit():
+    print("Quitting...")
+    kate.save_model(save_path)
+
+atexit.register(at_exit)
 
 def train_batch(data, batch_size, epoch=100, start_stop_info=True, progress_interval=5):
     n_batches = np.ceil(len(data) / batch_size)
@@ -38,7 +44,6 @@ def train_batch(data, batch_size, epoch=100, start_stop_info=True, progress_inte
 
 
 train_batch(data, 128, 100)
-kate.save_model(save_path)
 
 
 def random_sample(data, num_samples):

### 2017-12-03 dl_style_transfer/workspace/shallowCNN_reconstruct.py
Blah

@@ -26,7 +26,7 @@ tf.flags.DEFINE_string("positive_data_file", "./data/rt-polaritydata/rt-polarity
 tf.flags.DEFINE_string("negative_data_file", "./data/rt-polaritydata/rt-polarity.neg", "Data source for the negative data.")
 
 # Model Hyperparameters
-tf.flags.DEFINE_integer("embedding_dim", 128, "Dimensionality of character embedding (default: 128)")
+tf.flags.DEFINE_integer("embedding_dim", 14351, "Dimensionality of character embedding (default: 128)")
 tf.flags.DEFINE_string("filter_sizes", "3,4,5", "Comma-separated filter sizes (default: '3,4,5')")
 tf.flags.DEFINE_integer("num_filters", 128, "Number of filters per filter size (default: 128)")
 tf.flags.DEFINE_float("dropout_keep_prob", 0.5, "Dropout keep probability (default: 0.5)")
@@ -79,6 +79,27 @@ print("Vocabulary Size: {:d}".format(len(vocab_processor.vocabulary_)))
 print("Train/Dev split: {:d}/{:d}".format(len(y_train), len(y_dev)))
 
 
+def onehotencode(vector, num_classes=None):
+    """
+    Converts an input 1-D vector of integers into an output
+    2-D array of one-hot vectors, where an i'th input value
+    of j will set a '1' in the i'th row, j'th column of the
+    output array.
+    """
+    assert isinstance(vector, np.ndarray)
+    assert len(vector) > 0
+
+    if num_classes is None:
+        num_classes = np.max(vector)+1
+    else:
+        assert num_classes > 0
+        assert num_classes >= np.max(vector)
+
+    result = np.zeros(shape=(len(vector), num_classes))
+    result[np.arange(len(vector)), vector] = 1
+    return result.astype(int)
+
+
 # Training
 # ==================================================
 
@@ -109,10 +130,10 @@ with tf.Graph().as_default():
 
         # Expand data into the embeddings
         data_batch = x_train[:1]
+        vocab_size = len(vocab_processor.vocabulary_)
         embeddings_batch = np.zeros(data_batch.shape + (FLAGS.embedding_dim,))
-        n = len(vocab_processor.vocabulary_)
-        for i, sentence in enumerate(x_train):
-            embeddings_batch[i] = np.array(OneHotEncoder(n_values=n).fit_transform(np.array(sentence).reshape(1, -1)).todense()).reshape(-1, n)
[…]

### 2017-12-03 dl_style_transfer/train_kate_bag.py
nothing

@@ -1,8 +1,7 @@
 import numpy as np
+import atexit
 import os
 import sys
-import atexit
-
 sys.path.append(os.path.abspath('../'))
 
 import dl_style_transfer.from_shake_yelp as yelp

### 2017-12-04 dl_style_transfer/workspace/shallowCNN.py
Reconstruction stuff

@@ -7,9 +7,9 @@ class TextCNN(object):
     A CNN for text classification.
     Uses an embedding layer, followed by a convolutional, max-pooling and softmax layer.
     """
-    def __init__(
-      self, sequence_length, num_classes, vocab_size,
-      embedding_size, filter_sizes, num_filters, l2_reg_lambda=0.0):
+    def __init__(self, sequence_length, num_classes, vocab_size, embedding_size, filter_sizes,
+                 num_filters, l2_reg_lambda=0.0):
+
         self.sequence_length = sequence_length
         self.num_classes = num_classes
         self.vocab_size = vocab_size
@@ -40,14 +40,14 @@ class TextCNN(object):
                 filter_shape = [filter_size, embedding_size, 1, num_filters]
                 W = tf.get_variable("W", initializer=tf.truncated_normal(filter_shape, stddev=0.1))
                 b = tf.get_variable("b", initializer=tf.constant(0.1, shape=[num_filters]))
-                conv = tf.nn.conv2d(
+                self.conv = tf.nn.conv2d(
                     self.embedded_chars_expanded,
                     W,
                     strides=[1, 1, 1, 1],
                     padding="VALID",
                     name="conv")
                 # Apply nonlinearity
-                h = tf.nn.relu(tf.nn.bias_add(conv, b), name="relu")
+                h = tf.nn.relu(tf.nn.bias_add(self.conv, b), name="relu")
                 # Maxpooling over the outputs
                 pooled = tf.nn.max_pool(
                     h,

### 2017-12-04 dl_style_transfer/workspace/shallowCNN_reconstruct.py

@@ -10,7 +10,6 @@ from sklearn.preprocessing import OneHotEncoder
 
 import sys, os
 sys.path.append(os.path.abspath('../../'))
-import dl_style_transfer.layers.layers
 
 # Parameters
 # ==================================================

### 2017-12-04 dl_style_transfer/workspace/shallowCNN_transfer.py

@@ -4,7 +4,6 @@ import sys
 import os
 
 sys.path.append(os.path.abspath('../'))
-from dl_style_transfer.layers.layers import xavier_initializer
 
 
 class TextCNN(object):
@@ -13,9 +12,9 @@ class TextCNN(object):
     Uses an embedding layer, followed by a convolutional, max-pooling and softmax layer.
     """
 
-    def __init__(
-            self, num_reconstructions, sequence_length, num_classes, vocab_size,
-            embedding_size, filter_sizes, num_filters, l2_reg_lambda=0.0):
+    def __init__(self, num_reconstructions, sequence_length, num_classes, vocab_size, embedding_size, filter_sizes,
+                 num_filters, l2_reg_lambda=0.0):
+
         self.num_reconstructions = num_reconstructions
         self.sequence_length = sequence_length
         self.num_classes = num_classes
@@ -33,14 +32,14 @@ class TextCNN(object):
 
             self.reconstructions = tf.get_variable(
                 name="Reconstructions",
-                initializer=xavier_initializer([num_reconstructions, sequence_length, embedding_size]))
+                initializer=tf.random_uniform([num_reconstructions, sequence_length, embedding_size]))
             self.embedded_chars_expanded = tf.expand_dims(self.reconstructions, -1)
 
         # Create a convolution + maxpool layer for each filter size
         pooled_outputs = []
         self.activations = []
         for i, filter_size in enumerate(self.filter_sizes):
-            with tf.variable_scope("conv-maxpool-%s" % filter_size, reuse=True):
+            with tf.variable_scope("conv-maxpool-%s" % filter_size, reuse=tf.AUTO_REUSE):
                 # Convolution Layer
                 filter_shape = [filter_size, embedding_size, 1, num_filters]
                 W = tf.get_variable(name="W", shape=filter_shape, trainable=False)
@@ -73,7 +72,7 @@ class TextCNN(object):
             self.h_drop = tf.nn.dropout(self.h_pool_flat, self.dropout_keep_prob)
 
         # Final (unnormalized) scores and predictions
-        with tf.variable_scope("output", reuse=True):
+        with tf.variable_scope("output", reuse=tf.AUTO_REUSE):
             W = tf.get_variable(
                 "W", shape=[num_filters_total, num_classes], trainable=False)
             b = tf.get_variable(name="b", shape=[num_classes], trainable=False)

### 2017-12-04 dl_style_transfer/workspace/shallowCNN.py
Initial reconstructions

@@ -33,21 +33,23 @@ class TextCNN(object):
             self.embedded_chars_expanded = tf.expand_dims(self.embedded_chars, -1)
 
         # Create a convolution + maxpool layer for each filter size
-        pooled_outputs = []
+        self.convolved_outputs = []
+        self.pooled_outputs = []
         for i, filter_size in enumerate(filter_sizes):
             with tf.variable_scope("conv-maxpool-%s" % filter_size):
                 # Convolution Layer
                 filter_shape = [filter_size, embedding_size, 1, num_filters]
                 W = tf.get_variable("W", initializer=tf.truncated_normal(filter_shape, stddev=0.1))
                 b = tf.get_variable("b", initializer=tf.constant(0.1, shape=[num_filters]))
-                self.conv = tf.nn.conv2d(
+                conv = tf.nn.conv2d(
                     self.embedded_chars_expanded,
                     W,
                     strides=[1, 1, 1, 1],
                     padding="VALID",
-                    name="conv")
+                    name="conv" )
+                self.convolved_outputs.append(conv)
                 # Apply nonlinearity
-                h = tf.nn.relu(tf.nn.bias_add(self.conv, b), name="relu")
+                h = tf.nn.relu(tf.nn.bias_add(conv, b), name="relu")
                 # Maxpooling over the outputs
                 pooled = tf.nn.max_pool(
                     h,
@@ -55,11 +57,11 @@ class TextCNN(object):
                     strides=[1, 1, 1, 1],
                     padding='VALID',
                     name="pool")
-                pooled_outputs.append(pooled)
+                self.pooled_outputs.append(pooled)
 
         # Combine all the pooled features
         num_filters_total = num_filters * len(filter_sizes)
-        self.h_pool = tf.concat(pooled_outputs, axis=3)
+        self.h_pool = tf.concat(self.pooled_outputs, axis=3)
         self.h_pool_flat = tf.reshape(self.h_pool, [-1, num_filters_total])
 
         # Add dropout

### 2017-12-04 dl_style_transfer/workspace/shallowCNN_train_simplified.py

@@ -13,8 +13,8 @@ from tensorflow.contrib import learn
 
 # Data loading params
 tf.flags.DEFINE_float("dev_sample_percentage", .1, "Percentage of the training data to use for validation")
-tf.flags.DEFINE_string("positive_data_file", "./data/rt-polaritydata/rt-polarity.pos", "Data source for the positive data.")
-tf.flags.DEFINE_string("negative_data_file", "./data/rt-polaritydata/rt-polarity.neg", "Data source for the negative data.")
+tf.flags.DEFINE_string("positive_data_file", "../yelp_sentences.txt", "Data source for the positive data.")
+tf.flags.DEFINE_string("negative_data_file", "../runner_up.txt", "Data source for the negative data.")
 
 # Model Hyperparameters
 tf.flags.DEFINE_integer("embedding_dim", 128, "Dimensionality of character embedding (default: 128)")

### 2017-12-04 dl_style_transfer/workspace/shallowCNN_transfer.py

@@ -39,7 +39,7 @@ class TextCNN(object):
         pooled_outputs = []
         self.activations = []
         for i, filter_size in enumerate(self.filter_sizes):
-            with tf.variable_scope("conv-maxpool-%s" % filter_size, reuse=tf.AUTO_REUSE):
+            with tf.variable_scope("conv-maxpo  ol-%s" % filter_size, reuse=tf.AUTO_REUSE):
                 # Convolution Layer
                 filter_shape = [filter_size, embedding_size, 1, num_filters]
                 W = tf.get_variable(name="W", shape=filter_shape, trainable=False)

### 2017-12-04 dl_style_transfer/workspace/text-reconstruction.py

@@ -1,0 +1,95 @@
+import tensorflow as tf
+import numpy as np
+import os
+import sys
+import data_helpers
+from tensorflow.contrib import learn
+
+# Data Parameters
+tf.flags.DEFINE_string("positive_data_file", "../yelp_sentences.txt", "Data source for the positive data.")
+tf.flags.DEFINE_string("negative_data_file", "../runner_up.txt", "Data source for the negative data.")
+
+# Eval Parameters
+tf.flags.DEFINE_integer("batch_size", 64, "Batch Size (default: 64)")
+tf.flags.DEFINE_string("checkpoint_dir", "runs/1512363664/checkpoints", "Checkpoint directory from training run")
+tf.flags.DEFINE_boolean("eval_train", False, "Evaluate on all training data")
+
+# Misc Parameters
+tf.flags.DEFINE_boolean("allow_soft_placement", True, "Allow device soft device placement")
+tf.flags.DEFINE_boolean("log_device_placement", False, "Log placement of ops on devices")
+
+FLAGS = tf.flags.FLAGS
+FLAGS._parse_flags()
+
+x_text, y = data_helpers.load_data_and_labels(FLAGS.positive_data_file, FLAGS.negative_data_file)
+
+# Map data into vocabulary
+vocab_path = os.path.join(FLAGS.checkpoint_dir, "..", "vocab")
+vocab_processor = learn.preprocessing.VocabularyProcessor.restore(vocab_path)
+vocab_dict = vocab_processor.vocabulary_._mapping
+x_test = np.array(list(vocab_processor.transform(x_text)))
+
+test_idx = int(sys.argv[1])
+
+sequence_length = 144
+embedding_size = 128
+
+checkpoint_file = tf.train.latest_checkpoint(FLAGS.checkpoint_dir)
+graph = tf.Graph()
+
+with graph.as_default():
+    session_conf = tf.ConfigProto(allow_soft_placement=True, log_device_placement=False)
+    sess = tf.Session(config=session_conf)
+
+    with sess.as_default():
+        # Load the saved meta graph and restore variables
+        saver = tf.train.import_meta_graph("{}.meta".format(checkpoint_file))
+        saver.restore(sess, checkpoint_file)
+
+        # Get the placeholders from the graph by name
+        input_x = graph.get_operation_by_name("input_x").outputs[0]
+        dropout_keep_prob = graph.get_operation_by_name("dropout_keep_prob").outputs[0]
+
[…]

### 2017-12-04 dl_style_transfer/workspace/text-reconstruction.py
Text reconstruction

@@ -11,7 +11,7 @@ tf.flags.DEFINE_string("negative_data_file", "../runner_up.txt", "Data source fo
 
 # Eval Parameters
 tf.flags.DEFINE_integer("batch_size", 64, "Batch Size (default: 64)")
-tf.flags.DEFINE_string("checkpoint_dir", "runs/1512363664/checkpoints", "Checkpoint directory from training run")
+tf.flags.DEFINE_string("checkpoint_dir", "../runs/vanilla_cnn/checkpoints", "Checkpoint directory from training run")
 tf.flags.DEFINE_boolean("eval_train", False, "Evaluate on all training data")
 
 # Misc Parameters

### 2017-12-04 dl_style_transfer/workspace/text-reconstruction.py
Updated reconstructions

@@ -37,6 +37,9 @@ embedding_size = 128
 checkpoint_file = tf.train.latest_checkpoint(FLAGS.checkpoint_dir)
 graph = tf.Graph()
 
+checkpoint_file = tf.train.latest_checkpoint(FLAGS.checkpoint_dir)
+graph = tf.Graph()
+
 with graph.as_default():
     session_conf = tf.ConfigProto(allow_soft_placement=True, log_device_placement=False)
     sess = tf.Session(config=session_conf)
@@ -49,6 +52,8 @@ with graph.as_default():
         # Get the placeholders from the graph by name
         input_x = graph.get_operation_by_name("input_x").outputs[0]
         dropout_keep_prob = graph.get_operation_by_name("dropout_keep_prob").outputs[0]
+        W_emb_trained = sess.run(graph.get_operation_by_name("embedding/W").outputs[0])
+        W_emb = tf.constant(sess.run(graph.get_operation_by_name("embedding/W").outputs[0]))
 
         # Tensors we want to evaluate
         activations = []
@@ -87,9 +92,14 @@ with graph.as_default():
             for it in range(n_iters):
                 sess.run(train_step)
 
-        reconstructed = sess.run(reconstruction)
+        emb_distances = tf.matmul(tf.nn.l2_normalize(W_emb, dim=1),
+                                  tf.nn.l2_normalize(reconstruction[0], dim=1),
+                                  transpose_b=True)
+        token_ids = tf.argmax(emb_distances, axis=0)
+        # print(sess.run(token_ids))
+
         words = []
-        for idx in np.argmax(reconstructed, axis=-1).flatten():
+        for idx in sess.run(token_ids):
             words.append(list(vocab_dict.keys())[list(vocab_dict.values()).index(idx)])
         sentence_length = np.where(x_test[test_idx] == 0)[0][0]
         print(' '.join(word for word in words[:sentence_length]))

### 2017-12-14 dl_style_transfer/paper/main.tex

@@
 \alignauthor
-Luca Leeser\\
+Cameron Ibrahim\\
        \affaddr{Cornell University}\\
-       \email{ll698@cornell.edu}
+       \email{cai29@cornell.edu}
 \alignauthor
@@
 \alignauthor 
-Cameron Ibrahim\\
+Luca Leeser\\
        \affaddr{Cornell University}\\
-       \email{cai29@cornell.edu}
+       \email{ll698@cornell.edu}
 }
@@
 \begin{figure}[h]
-\subfloat{\includegraphics[width = .3\linewidth]{gates-hall.jpg}}
+\subfloat{\includegraphics[width=.3\linewidth]{gates-hall.jpg}}
 \hspace{0.1cm}
-\subfloat{\includegraphics[width = .3\linewidth]{starry_night.jpg}}
+\subfloat{\includegraphics[width=.3\linewidth]{starry_night.jpg}}
 \hspace{0.1cm}
-\subfloat{\includegraphics[width = .3\linewidth]{gates-starry.png}}
+\subfloat{\includegraphics[width=.3\linewidth]{gates-starry.png}}
 \caption{\textmd{Cornell's Gates Hall stylized in the form of Vincent Van Gogh's \textit{Starry Night}.}}
@@
 In this paper, we explore the use of $k$-competitive convolutional layers, a generalization of $k$-competitive layers designed for autoencoders in \cite{KATE}, which in turn are based on $k$-sparse layers as defined in \cite{MakhzaniF13}.
-These layers are integrated into a word-level convolutional neural network \cite{Kim14f}, and we perform a qualitative analysis of the quality of content and style representations generated by these networks.
+We hypothesize that this technique will allow us to mitigate the high-dimensional sparsity of textual data and reduce the problem of writing style transfer to the well-established field of image style transfer.
+We integrate $k$-competitive layers into preprocessing and training of a word-level convolutional neural network \cite{Kim14f}, and perform a qualitative analysis of the quality of content and style representations generated by these networks.
 A key benefit of our method is that it does not require a training set of translations between writing styles, which are very difficult to obtain.
@@
 Given the resources required to train a similarly robust classifier for text, we first explore the tradeoffs of using an underlying network that is trained to discriminate between a much smaller number of classes by training a VGG network with the CIFAR-10 dataset \cite{Krizhevsky09} (here, we use pre-trained weights provided by \cite{Liu15}).
-Although this modified network is far less generalizable in terms of classification, we found that the content representations provided by later layers of the network were still informative enough to reconstruct the original image, even for images containing objects not included in the 10 classes of CIFAR-10.
+Although this modified network is far less generalizable in terms of classification, we found that the content representations provided by later layers of the network were still informative enough to reconstruct the original image, even for images containing objects not included in the ten classes of CIFAR-10.
 By reconstruction, we refer to treating the input to the network as a variable, and minimizing $\ell_2$ loss between the input image and original image's feature representations in a certain layer.
@@
 \begin{figure}[h]
-\subfloat{\includegraphics[width = .15\linewidth]{cornell-campus-small.jpg}}
+\subfloat{\includegraphics[width=.15\linewidth]{cornell-campus-small.jpg}}
 \hspace{0.1cm}
-\subfloat{\includegraphics[width = .15\linewidth]{anderson-small.jpg}}
+\subfloat{\includegraphics[width=.15\linewidth]{anderson-small.jpg}}
 \hspace{0.1cm}
-\subfloat{\includegraphics[width = .15\linewidth]{boats.jpg}}
+\subfloat{\includegraphics[width=.15\linewidth]{boats.jpg}}
 \hspace{0.1cm}
-\subfloat{\includegraphics[width = .15\linewidth]{whale.jpg}}
+\subfloat{\includegraphics[width=.15\linewidth]{whale.jpg}}
 \hspace{0.1cm} 
-\subfloat{\includegraphics[width = .15\linewidth]{pizza.jpg}}
+\subfloat{\includegraphics[width=.15\linewidth]{pizza.jpg}}
 \hspace{0.1cm} \\
-\subfloat{\includegraphics[width = .15\linewidth]{2600.png}}
+\subfloat{\includegraphics[width=.15\linewidth]{2600.png}}
 \hspace{0.1cm}
-\subfloat{\includegraphics[width = .15\linewidth]{anderson5800.png}}
+\subfloat{\includegraphics[width=.15\linewidth]{anderson5800.png}}
 \hspace{0.1cm}
-\subfloat{\includegraphics[width = .15\linewidth]{boats2100.png}}
+\subfloat{\includegraphics[width=.15\linewidth]{boats2100.png}}
 \hspace{0.1cm}
-\subfloat{\includegraphics[width = .15\linewidth]{boats3200.png}}
+\subfloat{\includegraphics[width=.15\linewidth]{boats3200.png}}
 \hspace{0.1cm}
-\subfloat{\includegraphics[width = .15\linewidth]{pizza5000.png}}
+\subfloat{\includegraphics[width=.15\linewidth]{pizza5000.png}}
 \hspace{0.1cm} \\
-\subfloat{\includegraphics[width = .15\linewidth]{corne9900.png}}
+\subfloat{\includegraphics[width=.15\linewidth]{corne9900.png}}
 \hspace{0.1cm}
-\subfloat{\includegraphics[width = .15\linewidth]{ander9900.png}}
+\subfloat{\includegraphics[width=.15\linewidth]{ander9900.png}}
 \hspace{0.1cm}
-\subfloat{\includegraphics[width = .15\linewidth]{boats9900.png}}
+\subfloat{\includegraphics[width=.15\linewidth]{boats9900.png}}
 \hspace	{0.1cm}
-\subfloat{\includegraphics[width = .15\linewidth]{whale9900.png}}
+\subfloat{\includegraphics[width=.15\linewidth]{whale9900.png}}
 \hspace{0.1cm}
-\subfloat{\includegraphics[width = .15\linewidth]{pizza9900.png}}
+\subfloat{\includegraphics[width=.15\linewidth]{pizza9900.png}}
 \hspace{0.1cm}
@@
 However, we also observe that this reduction in generalizability of the underlying network architecture is not without tradeoffs.
-When using the conv4\_2 layer at which to match the feature representations of two images (the layer used in Figure 1), the reconstructed images are mostly unrecognizable to the human eye, and takes a much larger number of iterations to produce something even remotely close to the original.
-While we do not dismiss the possibility that this loss in reconstruction accuracy could be mitigated by hyperparameter optimization, we conclude that high generalizability as a classifier is an important quality of the underlying architecture although not paramount.
+When using conv4\_2 as the layer at which to match the feature representations of two images (the layer used in Figure 1), the reconstructed images are mostly unrecognizable, and it takes a much larger number of iterations to produce something even remotely close to the original.
+However, we believe that there is enough signal even within the unrecognizable images, and with further hyperparameter optimization we will be able to mitigate this loss in reconstruction accuracy.
+This justifies the use of networks for author classification that have been trained on a limited number of classes as a starting point.
 
@@
 \subsection{Convolutional Neural Networks for Text Classification}
-Although recurrent neural networks have proven adept at language recognition tasks, evaluating the overall content and style of written text is a task that is less dependent on sequential information, and a hidden state is likely too small to encode enough information for our purposes.
+Although recurrent neural networks have proven adept at language recognition tasks, evaluating the overall content and style of written text is a task that is less dependent on sequential information (outside the scope of a receptive field), and a hidden state is likely too small to encode enough information for our purposes.
 We believe that a a convolutional neural network allows us to take advantage of the success of style transfer for images, in contrast to aforementioned approaches that treat style transfer as a machine translation problem.
@@
 After identifying the most frequent reviewers, we tokenize all of their reviews using NLTK \cite{Loper02nltk:the} to generate a corpus.
+To create a baseline task, we also create a corpus of Shakespearean works from Project Gutenberg\footnote{{\texttt{https://www.gutenberg.org/}}}.
 
 \subsection{Comparison of Architectures}
+We explore the use of $k$-competitive layers in two settings: in an autoencoder to generate word embeddings, and as a non-linearity after convolutional layers.
+
+\subsubsection{K-Competitive Autoencoder for Embeddings}
+In natural language processing tasks it is common encode textual data into a sparse space before generating embeddings that project these word or sentence-level vectors into a lower dimensional space.
+The $k$-competitive autoencoder for text (KATE) proposed in \cite{KATE} generates word embeddings that compare favorably to the more commonly used word2vec \cite{Mikolov13}, and we explore its use as a preprocessing step for an convolutional author classifier network.
+The two variants that we explore are in the initial sparse representation of training data: we compare between the use of a sentence-level log-normalized word count vectors similar to \cite{KATE} and word-level one-hot encoded vectors.
+
+Since the autoencoder is used to generate vector embeddings of words, it can be argued that using sentence-level embeddings as training data creates a model that is asked to perform different tasks at training and test time.
+At the same time, these log-normalized word count vectors contain entries between 0 and 1, and can therefore be interpreted as probabilities of potentially overlapping classes.
+Compared to the one-hot encoding approach that treats words as belonging in mutually exclusive classes, this approach more accurately reflects the reality that words often have overlapping meanings.
+The amount of training data produced from a single passage of text depends on the relative magnitudes of the number of unique words and number of unique sentences, but given an even ratio the word count approach likely produces more useful data - a single word is much more likely to be meaningless noise than a sentence.
+
+Consistent with the probabilistic interpretation mentioned above, we swap the sigmoid activation function used in the word count approach for a softmax function when using one-hot encoding.
+We explore the tradeoffs between these two approaches, and quantitatively assess their performance by comparing reconstruction accuracy of the autoencoder, that is, the $\ell_2$ loss between the input vector and the decoded vector of its low dimensional representation.
+
+\subsubsection{K-Competitive Layer as Activation Function}
+Both convolutional and fully connected $k$-competitive layers are non-linear functions and are therefore appropriate as activation functions.
+Since they set the activations of the least active neurons to 0, these act similarly to a rectified linear unit with an adaptive threshold.
+As with ReLU, this property enforces sparsity among the coefficients and therefore acts both as a regularizer and non-linearity.
+Meanwhile, the allocation of energy from ``loser'' to ``winner'' nodes prevents these neurons from becoming entirely dead and preserves gradient flow in backpropagation.
+Since the baseline convolutional architecture is shallow and only has one convolutional layer (albeit many filters), we add one $k$-competitive layer following the convolutional layer, with a ReLU layer following it to preserve the non-linearity at inference time (the $k$-competitive layer is defined as the identity function at test time in \cite{KATE}).
+The classification tasks are: the baseline tasks of differentiating Shakespearean text from the most prolific Yelp reviewer; differentiating between the two most prolific Yelp reviewers.
+
+We compare the performance of the following model configurations on two author classification tasks: the baseline convolutional network with one-hot encoded vectors as input; the baseline convolutional neural network with KATE embedded vectors as input; a convolutional neural network with a $k$-competitive layer taking one-hot encoded vectors as input.
 
 \subsection{Hyperparameters and Training}
+All models were implemented in TensorFlow and trained on a TITAN Xp GPU.
+Our implementation of the convolutional neural network from \cite{Kim14f} is credited to Denny Britz\footnote{{\texttt{https://github.com/dennybritz}}}.
+Both variations of the $k$-competitive autoencoder were trained with a bottleneck layer of size 128, $k=32$, amplification constant $\alpha=6.26$ \cite{KATE}, learning rate 0.001, 100 epochs, and a batch size of 128 using the Adam optimizer \cite{KingmaB14}.
+All variations of the convolutional network were trained with dropout rate 0.5, $\ell_2$ regularization parameter $\lambda=0$, learning rate 0.001, 200 epochs, and a batch size of 64 using the Adam optimizer.
+Variations with the $k$-competitive layer used $k=32, 64$ and $\alpha=6.26$.
 
@@
 \section{Future Extensions}
+Varying length of what is considered a single ``document'' on which to generate word count vector for KATE.
 
@@
 % APPENDIX
-%pagebreak
+\begin{appendix}
+All code associated with this paper can be found here.
+\end{appendix}
 
-\begin{appendix}
-%\href{https://github.com/CornellDataScience/Yelp-FA17/tree/master/dl_style_transfer}{Link} to Github repository for all code associated with this paper.
+\balance
 
-\end{appendix}
 \end{document}
